### 2023-10-19 about.qmd
Update

---
title: "Data Story"
---

<br>

### Investigating Singapore's Resale Flat Prices from 1990 to 2023

##### Is public housing in Singapore affordable for the average Singaporean?

<br> This is where my introduction will be. This is just a placeholder for potential data sets!

```{r, eval=TRUE,echo=FALSE}
library(tidyverse)
starwars
```

### 2023-10-19 index.qmd
Update

---
title: ""
---

```{r, eval=TRUE,echo=FALSE}

```

![](images/namelogo.png)

#

# [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}

```{r, eval=TRUE,echo=FALSE}

library(grid)
library(gridExtra)
library(png)

img1 <- readPNG("src/images//me_icon.png")
img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")

grid.arrange(rasterGrob(img1, width=unit(1.1,"npc"), height=unit(0.8,"npc"), gp=gpar(mai=c(0,0,0,0))), 
             rasterGrob(img2, width=unit(1,"npc"), height=unit(0.7,"npc"), gp=gpar(mai=c(0,0,0,0))), 
             ncol=2)

```

# **My Hello to You \~**

Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 2nd year, double majoring in Sociology and, Communications and New Media!

I have always been fascinated by how society functions and its intricate connections, my passion for understanding the world around us, is driven by a desire to foster meaningful connections within all communities!

To demonstrate this, I embark of frequent backpacking trips across Southeast Asia, and actively engage myself in the cultures and learn about their customs.

Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities. Here's a little snippet!

```{=html}
<style>
    .tiktok-container {
        display: flex;
        justify-content: center;
        align-items: center;
        gap: 20px; /* Adjust for spacing between the embeds */
    }

    .tiktok-embed {
        width: 50%; /* Adjust based on your desired width */
        max-width: none;
    }
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">

<section>

<a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>

<p>overland travel for the vibesss. what a way to end 2022 phewww</p>

<a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>

</section>

</blockquote>

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
> </blockquote>

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7238779076528442625" data-video-id="7238779076528442625" style="max-width: 605px;min-width: 325px;">

<section>

<a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>

<p>nha trang is my favvvvvv</p>

<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>

</section>

</blockquote>

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
:::

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
# **My Past Work**

## National University of Singapore

### DTK1234 - Design Thinking

In this module, we were assigned the task of innovating everyday chores. Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe

![](images/prototyping.png){fig-align="center"}

The actual prototyping journey was not very smooth, but hey, here is the end product! Looks good aye? To me at least...

![](images/prototyping_2-01.png)

## Temasek Polytechnic

### Savvify - An Automated Savings Platform

During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***. Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.

Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!

{{< video https://youtu.be/kzWq31_mRyc >}}

### GIGAWipes - Innovation through Programming

"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives. This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but... I'll let the video do the talking...

{{< video https://youtu.be/2yBwaRCfiuI >}}

#

```         
```

### 2023-10-19 index.qmd
Update
Update index.qmd
Project Update

@@
 
-![](images/namelogo.png)
+![](src/images/namelogo.png)
 
-#
-
-# [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}
+### [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}
 
@@
 
-img1 <- readPNG("src/images//me_icon.png")
+img1 <- readPNG("src/images/me_icon.png")
 img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")

### 2023-10-20 index.qmd
Update
update

@@
 ---
-title: ""
+title: "Marzuki Nooranas"
 ---
@@
 ```
-
-![](src/images/namelogo.png)
 
@@
   display: flex;
+  flex-wrap: wrap;
   justify-content: center;
-        align-items: center;
-        gap: 20px; /* Adjust for spacing between the embeds */
 }
@@
 .tiktok-embed {
-        width: 50%; /* Adjust based on your desired width */
-        max-width: none;
+  max-width: 100%;
+  flex: 1 1 300px;
+}
+
+@media screen and (max-width: 600px) {
+  .tiktok-embed {
+    min-width: auto;
+  }
 }
@@
 
-```{=html}
-<script async src="https://www.tiktok.com/embed.js"></script>
-```
 # **My Past Work**

### 2023-10-20 index.qmd
Update
update

@@
 Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities.
-Here's a little snippet!
+Here's a little snippet - My overland journey from Singapore to Vietnam!
 
@@
 
-<p>overland travel for the vibesss. what a way to end 2022 phewww</p>
-
-<a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>
+<p>overland travel for the vibesss </p>
 
@@
 <p>nha trang is my favvvvvv</p>
-
-<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>
 

### 2023-10-20 index.qmd
update

--- 2023-10-20 index.qmd
@@
 <style>
+body, html {
+  margin: 0;
+  padding: 0;
+  overflow-x: hidden; /* prevent horizontal scroll */
+}
+
 .tiktok-container {
@@
   justify-content: center;
+  width: 100%; /* ensure the container takes the full width */
 }
@@
 .tiktok-embed {
+  box-sizing: border-box; /* make sure padding and borders are included in total width */
   max-width: 100%;
   flex: 1 1 300px;
+  margin: 0 auto; /* center the blockquote */
 }
@@
 
-<p>overland travel for the vibesss. what a way to end 2022 phewww</p>
+<p>overland travel for the vibesss </p>
 

### 2023-10-20 index.qmd
Update

--- 2023-10-20 index.qmd
@@
 
+## My overland journey from Singapore to Vietnam!
+
 To demonstrate this, I embark of frequent backpacking trips across Southeast Asia, and actively engage myself in the cultures and learn about their customs.
@@
 Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities.
-Here's a little snippet!
+Here's a little snippet -
 
@@
 <style>
+body, html {
+  margin: 0;
+  padding: 0;
+  overflow-x: hidden; 
+}
+
 .tiktok-container {
@@
   justify-content: center;
+  width: 105%; 
 }
@@
 .tiktok-embed {
+  box-sizing: border-box;
   max-width: 100%;
   flex: 1 1 300px;
+  margin: 0 auto; 
 }
@@
 
-<p>overland travel for the vibesss. what a way to end 2022 phewww</p>
+<p>overland travel for the vibesss</p>
 

### 2023-10-27 about.qmd
Project Update

@@
 ---
+
+## Is Public Housing in Singapore Affordable for the Average Singaporean?
 
@@
 
-##### Is public housing in Singapore affordable for the average Singaporean?
+In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD \$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
+While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
 

### 2023-11-03 datastory.qmd
Weekly Update

---
title: "Singapore's Public Housing Affordability"
---

![](src/images/HDB-flat-after-divorce.jpg){width="698"}

## Is Public Housing in Singapore Affordable for the Average Singaporean?

### Investigating Singapore's Resale Flat Prices from 1990 to 2023

<p>

</p>

In Singapore, housing affordability has been an increasing worry for future Singaporeans. However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD \$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012). While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.

<p>

</p>

### Trend of HDB Resale Prices in Singapore

<p>

</p>

Line and Bar Graph

```{r, eval=TRUE,echo=FALSE}
library(shiny)
library(ggplot2)

# Placeholder example using the pressure dataset
ggplot(pressure, aes(x = temperature, y = pressure)) +
  geom_line() +
  labs(title = "Title", x = "x-axis", y = "y-axis")
```

### The Distribution of Resale Flat Prices of Different Flat Types

<p>

</p>

Box Plot Placeholder

```{r, eval=TRUE,echo=FALSE}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot() +
  labs(title = "Title", 
       x = "x-axis", 
       y = "y-axis")

```

### The Impact of Remaining Lease on Resale Prices

<p>

</p>

Scatter Plot

```{r, eval=TRUE,echo=FALSE}

ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(title = "Title", 
       x = "x-axis", 
       y = "y-axis")
```

### The influence of Estate on Resale Prices

<p>

</p>

Violin Plot

```{r, eval=TRUE,echo=FALSE}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_violin(trim=FALSE) +
  labs(title = "TITLE", 
       x = "x-axis", 
       y = "y-axis")

```

### Assessing Affordability of Resale Flats in Singapore

<p>

</p>

Still considering

```{r, eval=FALSE,echo=FALSE}

```

### Conclusion

<p>

</p>

```{r, eval=TRUE,echo=FALSE}

```

```{r}

```

### 2023-11-06 datastory.qmd
Weekly Update

@@
 
+```{r, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
+# Load the required libraries
+library(tidyverse)
+library(tidyr)
+library(ggplot2)
+library(scales)
+```
+
 ```{r, eval=TRUE,echo=FALSE}
-library(shiny)
-library(ggplot2)
+# Load the datasets
+data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
+data2022 <- read.csv("docs/src/data/ResaleFlatPrices2022.csv")
 
-# Placeholder example using the pressure dataset
-ggplot(pressure, aes(x = temperature, y = pressure)) +
+average_prices_1999 <- data1999 %>%
+  group_by(flat_type) %>%
+  summarise(AveragePrice1999 = mean(resale_price))
+
+average_prices_2022 <- data2022 %>%
+  group_by(flat_type) %>%
+  summarise(AveragePrice2022 = mean(resale_price))
+
+combined_data <- merge(average_prices_1999, average_prices_2022, by = "flat_type")
+
+long_data <- pivot_longer(combined_data, cols = -flat_type, names_to = "Year", values_to = "AveragePrice")
+
+ggplot(long_data, aes(x = flat_type, y = AveragePrice, group = Year, color = Year)) +
   geom_line() +
-  labs(title = "Title", x = "x-axis", y = "y-axis")
+  geom_point() +
+  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = 1, check_overlap = TRUE) +
+  scale_y_continuous(labels = label_comma()) + 
+  labs(title = "Average Resale Price Increment for Each Flat Type (1999 vs 2022)",
+       x = "Flat Type",
+       y = "Average Resale Price",
+       color = "Year") +
+  theme_minimal()
+
 ```

### 2023-11-06 datastory.qmd
Update datastory.qmd

@@
 ```{r, eval=TRUE,echo=FALSE, message=FALSE, warning=FALSE}
-# Load the required libraries
+
 library(tidyverse)
@@
 ```{r, eval=TRUE,echo=FALSE}
-# Load the datasets
 data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")

### 2023-11-06 datastory.qmd
Weekly Update

@@
 
-### Investigating Singapore's Resale Flat Prices from 1990 to 2023
-
-<p>
-
+### Investigating Singapore's Resale Flat Prices from 1990 to 2022
+<p></p>
+<p style="text-align: justify;">
+In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
+While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
 </p>
 
-In Singapore, housing affordability has been an increasing worry for future Singaporeans.
-However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD \$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
-While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
-
-<p>
-
+<p style="text-align: justify;">
+Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
+This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.
+The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
 </p>
-
 ### Trend of HDB Resale Prices in Singapore
@@
 </p>
-
-Line and Bar Graph
 
@@
   group_by(flat_type) %>%
-  summarise(AveragePrice1999 = mean(resale_price))
+  summarise(Mean1999 = mean(resale_price))
 
@@
   group_by(flat_type) %>%
-  summarise(AveragePrice2022 = mean(resale_price))
+  summarise(Mean2022 = mean(resale_price))
 
@@
   geom_point() +
-  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = 1, check_overlap = TRUE) +
+  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = -1, check_overlap = TRUE, size = 3) +
   scale_y_continuous(labels = label_comma()) + 
-  labs(title = "Average Resale Price Increment for Each Flat Type (1999 vs 2022)",
+  labs(title = "Average Resale Price Each Flat Type in 1999 and 2022 in SG Dollars",
        x = "Flat Type",
@@
 ```
+<p style="text-align: justify;">
+To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
+The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
+</p>
+
+<p>
+
+</p>
+
+-   Talk about how the slopes got steeper.
+-   There is a bigger price gap from each flat type to the next flat type.
+-   Compare the price differences on each flat type.
+-   Do some calculations here
+-   Make an interactive shiny for bar graph
 

### 2023-11-09 datastory.qmd
Weekly Update

@@
 
-```{r, eval=TRUE,echo=FALSE}
+```{r, eval=TRUE,echo=FALSE, fig.align='center'}
 data1999 <- read.csv("docs/src/data/ResaleFlatPrices1999.csv")
@@
   group_by(flat_type) %>%
-  summarise(Mean1999 = mean(resale_price))
+  summarise("1999" = mean(resale_price))
 
@@
   group_by(flat_type) %>%
-  summarise(Mean2022 = mean(resale_price))
+  summarise("2022" = mean(resale_price))
 
@@
 ggplot(long_data, aes(x = flat_type, y = AveragePrice, group = Year, color = Year)) +
-  geom_line() +
-  geom_point() +
-  geom_text(aes(label = round(AveragePrice, 2)), hjust = 1, vjust = -1, check_overlap = TRUE, size = 3) +
+  geom_line(linewidth = 1.5) +
+  geom_point(size = 3) +
+  geom_text(aes(label = sprintf("$%.2f", AveragePrice)), hjust = 1, vjust = -1, check_overlap = TRUE, size = 3) +
   scale_y_continuous(labels = label_comma()) + 
-  labs(title = "Average Resale Price Each Flat Type in 1999 and 2022 in SG Dollars",
+  labs(title = "Average Resale Price in 1999 and 2022 (Flat Type, SGD)",
        x = "Flat Type",
@@
 ```
+
 <p style="text-align: justify;">
@@
 The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
+Before moving on to the deeper analysis
 </p>
@@
 
+Interactive Bar Graph Placeholder
+
+```{r, eval=TRUE,echo=FALSE}
+
+library(ggplot2)
+
+data <- data.frame(
+  category = c("A", "B", "C", "D"),
+  value = c(23, 45, 12, 78)
+)
+
+ggplot(data, aes(x = category, y = value)) +
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  labs(title = "Simple Bar Graph", x = "Category", y = "Value")
+
+```
+<p></p>
 ### The Distribution of Resale Flat Prices of Different Flat Types

### 2023-11-10 datastory.qmd
Weekly Update

@@
 
-![](src/images/HDB-flat-after-divorce.jpg){width="698"}
-
+```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center'}
+knitr::include_graphics("src/images/HDB-flat-after-divorce.jpg")
+```
 ## Is Public Housing in Singapore Affordable for the Average Singaporean?
@@
 ### Investigating Singapore's Resale Flat Prices from 1990 to 2022
-<p></p>
+
+<p>
+
+</p>
+
 <p style="text-align: justify;">
+
 In Singapore, housing affordability has been an increasing worry for future Singaporeans.
@@
 While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
@@
 The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
+
+According to Kumar (2022),
 </p>
+
+```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center', fig.cap="Estimation of Average Salary Per Spouse (Kumar, 2022)"}
+knitr::include_graphics("docs/images/dreamhome.png")
+```
+
 ### Trend of HDB Resale Prices in Singapore
@@
 <p style="text-align: justify;">
+
 To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
@@
 Before moving on to the deeper analysis
+
 </p>
@@
 ```
-<p></p>
+
+<p>
+
+</p>
+
 ### The Distribution of Resale Flat Prices of Different Flat Types

### 2023-11-14 datastory.qmd
Weekly Update

@@
 
-```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center'}
-knitr::include_graphics("src/images/HDB-flat-after-divorce.jpg")
-```
-## Is Public Housing in Singapore Affordable for the Average Singaporean?
+![](src/images/HDB-flat-after-divorce.jpg){width="698"}
+
+## Is Public Housing Affordable for Singaporeans?
 
@@
 
-According to Kumar (2022),
 </p>
 
-```{r, out.height= "200px",out.width="800px",echo=FALSE,eval=TRUE, fig.align='center', fig.cap="Estimation of Average Salary Per Spouse (Kumar, 2022)"}
-knitr::include_graphics("docs/images/dreamhome.png")
-```
+<p style="text-align: justify;">
+
+According to Kumar (2022),
+
+</p>
+
+![](docs/images/dreamhome.png){width="698"}
+
+<p style="text-align: justify;">
+
+To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
+The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
+Before moving on to the deeper analysis
+
+</p>
 
@@
 
-<p style="text-align: justify;">
-
-To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
-The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
-Before moving on to the deeper analysis
-
-</p>
-
 <p>
@@
 Interactive Bar Graph Placeholder
+
+<iframe height="400" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/example/"></iframe>
 

### 2023-11-14 datastory.qmd
Project Update

@@
 <p style="text-align: justify;">
-
 In Singapore, housing affordability has been an increasing worry for future Singaporeans.
@@
 While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
@@
 The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
-
 </p>
@@
 <p style="text-align: justify;">
-
 According to Kumar (2022),
-
 </p>
 
+<p style="text-align: justify;">
 ![](docs/images/dreamhome.png){width="698"}
-
+</p>
 <p style="text-align: justify;">
-
 To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
@@
 Before moving on to the deeper analysis
-
 </p>
@@
 
-<p>
-
+<p style="text-align: justify;">
 </p>
@@
   group_by(flat_type) %>%
-  summarise("1999" = mean(resale_price))
+  summarise("1990" = mean(resale_price))
 
@@
   scale_y_continuous(labels = label_comma()) + 
-  labs(title = "Average Resale Price in 1999 and 2022 (Flat Type, SGD)",
+  labs(title = "Average Resale Price in 1990 and 2022 (Flat Type, SGD)",
        x = "Flat Type",
@@
 
-<p>
+<p style="text-align: justify;">
 
@@
 Interactive Bar Graph Placeholder
-
-<iframe height="400" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/example/"></iframe>
 
@@
 
-```{r, eval=TRUE,echo=FALSE}
-ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
-  geom_boxplot() +
-  labs(title = "Title", 
-       x = "x-axis", 
-       y = "y-axis")
-
-```
+<iframe height="450" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/boxplot/"></iframe>
 

### 2023-11-14 boxplot/boxplot.R

@@ -1,0 +1,63 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(scales)
+
+#combining two files to for comparisonnn
+combine_data <- function(data1990_path, data2022_path) {
+  data1990 <- read.csv(data1990_path)
+  data2022 <- read.csv(data2022_path)
+  
+  #change format from yyyy-mm to yyyy
+  data1990$Year <- as.numeric(substr(data1990$month, 1, 4))
+  data2022$Year <- as.numeric(substr(data2022$month, 1, 4))
+  combinedData <- rbind(data1990, data2022)
+  
+  return(combinedData)
+}
+
+# Define UI
+ui <- fluidPage(
+  titlePanel(""),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("flatType", "Select Flat Type:", 
+                  choices = c("3 ROOM", "4 ROOM", "5 ROOM", "EXECUTIVE"), 
+                  selected = "3 ROOM",
+                  multiple = TRUE), #this defaults to 3 room
+      checkboxGroupInput("year", "Select Year(s):",
+                         choices = c('1990', '2022'),
+                         selected = c('1990', '2022'))
+    ),
+    mainPanel(
+      plotOutput("boxPlot")
+    )
+  )
+)
+
+# Define Server Logic
+server <- function(input, output, session) {
+  combinedData <- combine_data("www/ResaleFlatPrices1999.csv", "www/ResaleFlatPrices2022.csv")
+  
+  updateSelectInput(session, "flatType", 
+                    choices = unique(combinedData$flat_type),
+                    selected = unique(combinedData$flat_type)[1])
+  
+  output$boxPlot <- renderPlot({
+    filteredData <- filter(combinedData, 
+                           flat_type %in% input$flatType,
+                           Year %in% as.numeric(input$year))
+    
+#boxplot creation
+    ggplot(filteredData, aes(x = flat_type, y = resale_price, fill = as.factor(Year))) +
+      geom_boxplot() +
+      scale_y_continuous(labels = label_dollar()) + 
+      theme_minimal() +
+      labs(title = "Box Plot of Resale Prices", 
+           y = "Resale Price", x = "Flat Type") +
+      scale_fill_brewer(palette = "Set2", name = "Year") 
+  })
+}
+
+shinyApp(ui, server)
+

### 2023-11-14 interactivebar/interactivebar.R

@@ -1,0 +1,69 @@
+library(shiny)
+library(ggplot2)
+library(dplyr)
+library(scales) # for currency formatting
+
+# Define global data combining function to be used in server
+combine_data <- function(data1990_path, data2022_path) {
+  # Load the datasets
+  data1990 <- read.csv(data1990_path)
+  data2022 <- read.csv(data2022_path)
+  
+  # Add a 'Year' column to both datasets to identify them after combining
+  data1990$Year <- as.numeric(substr(data1990$month, 1, 4))
+  data2022$Year <- as.numeric(substr(data2022$month, 1, 4))
+  
+  # Combine the two datasets
+  combinedData <- rbind(data1990, data2022)
+  
+  return(combinedData)
+}
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Resale Flat Prices Box Plot"),
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("flatType", "Select Flat Type:", 
+                  choices = c("3 ROOM", "4 ROOM", "5 ROOM", "EXECUTIVE"), # Specify the types you want to include
+                  selected = "3 ROOM",
+                  multiple = TRUE),
+      checkboxGroupInput("year", "Select Year(s):",
+                         choices = c('1990', '2022'),
+                         selected = c('1990', '2022'))
+    ),
+    mainPanel(
+      plotOutput("boxPlot")
+    )
+  )
+)
+
+# Define Server Logic
+server <- function(input, output, session) {
+  # Call the global data combining function
+  combinedData <- combine_data("www/ResaleFlatPrices1999.csv", "www/ResaleFlatPrices2022.csv")
+  
+  # Update the choices for selectInput based on the combined data
+  updateSelectInput(session, "flatType", 
+                    choices = unique(combinedData$flat_type),
+                    selected = unique(combinedData$flat_type)[1])
+  
+  output$boxPlot <- renderPlot({
+    # Filter data based on selected flat type and year(s)
+    filteredData <- filter(combinedData, 
+                           flat_type %in% input$flatType,
+                           Year %in% as.numeric(input$year))
+    
+    # Create box plot
+    ggplot(filteredData, aes(x = flat_type, y = resale_price, fill = as.factor(Year))) +
+      geom_boxplot() +
+      scale_y_continuous(labels = label_dollar()) + # Format the y axis as dollar
+      theme_minimal() +
[…]

### 2023-11-14 datastory.qmd
Project Update

@@
 
-![](src/images/HDB-flat-after-divorce.jpg){width="698"}
+![](src/images/HDB-flat-after-divorce.jpg){fig-align="left" width="1000"}
 
@@
 
-<p>
-
+<p style="text-align: justify;">
+In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
 </p>
@@
 <p style="text-align: justify;">
-In Singapore, housing affordability has been an increasing worry for future Singaporeans.
-However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
 While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
@@
 This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.
+</p>
+
+<p style="text-align: justify;">
 The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
@@
 
+![](docs/images/dreamhome.png){fig-align="center" width="698"}
+
 <p style="text-align: justify;">
-According to Kumar (2022),
+According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue.
+The table below provides an outline of the housing prices in Singapore.
+Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.
 </p>
@@
 <p style="text-align: justify;">
-![](docs/images/dreamhome.png){width="698"}
+For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at lease earn SGD\$5,230.
+While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
 </p>
+
 <p style="text-align: justify;">
-To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
-The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
-Before moving on to the deeper analysis
+Imagine you and your sponse are looking to start a family.
+Now that we've a glimpse into the affordability of homes in Singapore, do you think you can comfortably own your own home when the time comes?
+Let's dive into real data and discuss this critical issue further.
 </p>
@@
 <p style="text-align: justify;">
+To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
+The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
+</p>
+
+<p style="text-align: justify;">
+Before moving on to the deeper analysis, let us understand how the overall prices have increased from 1990 to 2022.
+While the general increase in prices overtime aligns with economic growth, the rate of the surge from 1990 to 2022 is alarming.
+</p>
+
+<p style="text-align: justify;">
+One may argue that the increment is a sign of prospering economy, on the other side, it also rings alarm bells in terms of overall affordability. Now let's examine the graph below:
 </p>
@@
 <p style="text-align: justify;">
-
+The graph above illustrates a significant steepening in the slopes of average resale prices in Singapore from 1990 to 2022 - indicating the exorbitant increase of prices across all flat types.
+The steeper slope in 2022 shows a more prominent price escalation as compared to 1990's.
+This is can be an indication increasing pressure on affordability and financial stretch for home ownership.
 </p>
 
--   Talk about how the slopes got steeper.
--   There is a bigger price gap from each flat type to the next flat type.
--   Compare the price differences on each flat type.
--   Do some calculations here
--   Make an interactive shiny for bar graph
+<p style="text-align: justify;">
+Notice that on the graph, there is a worrying widening price gap between each successive flat type, with the difference in average prices from one flat type to the next becoming more distinct.
+For example, the price jump from a 3-room to a 4-room for both 1990 and 2022, may point towards a growing demand for a larger home.
+Larger home, bigger family right?
+</p>
 
-Interactive Bar Graph Placeholder
+<p style="text-align: justify;">
+With that, we can understand that the widening gap of prices could create a cost burden for upgraders seeking more specious accommodations for a bigger family.
+The growing gap in prices shows that planning for home ownership is extremely crucial to prevent any buyers' remorse.
+</p>
+
+<p style="text-align: justify;">
+Now let's look at the price increment individually for both years, compared with the same flat type. 
+</p>
 
@@
 
-<p style="text-align: justify;">
-</p>
-
 ### The Distribution of Resale Flat Prices of Different Flat Types
@@
 <p style="text-align: justify;">
-
+While a price increment can potentially indicate a critical issue with affordability, it is also important to access where the increase is still within the "safe" median range.
+However, in the box plot below, we can see how the presence of outliers underscores the significant and unprecedented price increase.
 </p>
 
-Box Plot Placeholder
+<p style="text-align: justify;">
+Hint: Pay attention to how 3-room flats almost hitting $1,000,000!
+On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively.
+</p>
 
-<iframe height="450" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/boxplot/"></iframe>
+<iframe height="500" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/boxplot/">
+
+</iframe>
+
+<p style="text-align: justify;">
+Let's input all the flat type options, what do you see?
+With 3-Room, 4-Room, 5-Room and Executive selected, we can see a consistent pattern.
+The data reveals a distinct trend where "regular-sized" flats are slowly approaching the million-dollar mark in resale price in 2022.
+The upward trajectory is also an indication of the growth in the resale market, reflecting how people are willing to pay for their dream home.
+This inevitably affect those within a lower income bracket, preventing them to do the same.
+<p>
+
+<p style="text-align: justify;">
+Furthermore, across the other flat types, there is an increasing number of outliers beyond the upper whiskers of the box plots for 2022.
+While this can suggest a substantial market growth, it can also reflect the high number of exceptional cases where resale prices are charging a even higher premium, exceeding the median trends - which is already high.
+</p>
+
+<p style="text-align: justify;">
+Now, that we have clearly seen the high prices Singaporean are willing to pay for their dream home, are there other factors that can be attributed to the price increase?
+Next, we will explore if the remaining lease left or the location of the flat affect the resale price.
+</p>
 
@@
 <p style="text-align: justify;">
-
+To lower the cost burden for flat upgraders, some may consider purchasing a flat with a lower remaining lease.
+However, is there a correlation between the remaining lease and the cost of a resale flat?
 </p>
-
-Scatter Plot
 
@@
 <p style="text-align: justify;">
+We can agree that price is an important consideration for purchasing a home.
+Have you figured out where to live?
+Do you want to live close to your parents in the same estate?
+Or do you have a preferred school you would like to send your future children too?
 </p>
 
-Violin Plot
+<p style="text-align: justify;">
+Now, we will examine if the estate affects the price of the resale flat. We will also determine which estate tends to be more costly or cheaper to settle down. 
+</p>
 
@@
 
-<p style="text-align: justify;">
-
-</p>
-
-Still considering
-
 ```{r, eval=FALSE,echo=FALSE}
@@
 
-<p style="text-align: justify;">
-
-</p>
-
 ```{r, eval=TRUE,echo=FALSE}
@@
 
+### References
 ```{r}

### 2023-11-14 boxplot/boxplot.R

@@ -3,7 +3,7 @@ library(ggplot2)
 library(dplyr)
 library(scales)
 
-#combining two files to for comparisonnn
+#combining two files to for comparison
 combine_data <- function(data1990_path, data2022_path) {
   data1990 <- read.csv(data1990_path)
   data2022 <- read.csv(data2022_path)

### 2023-11-14 interactivebar/interactivebar.R

@@ -1,69 +1,0 @@
-library(shiny)
-library(ggplot2)
-library(dplyr)
-library(scales) # for currency formatting
-
-# Define global data combining function to be used in server
-combine_data <- function(data1990_path, data2022_path) {
-  # Load the datasets
-  data1990 <- read.csv(data1990_path)
-  data2022 <- read.csv(data2022_path)
-  
-  # Add a 'Year' column to both datasets to identify them after combining
-  data1990$Year <- as.numeric(substr(data1990$month, 1, 4))
-  data2022$Year <- as.numeric(substr(data2022$month, 1, 4))
-  
-  # Combine the two datasets
-  combinedData <- rbind(data1990, data2022)
-  
-  return(combinedData)
-}
-
-# Define UI
-ui <- fluidPage(
-  titlePanel("Resale Flat Prices Box Plot"),
-  sidebarLayout(
-    sidebarPanel(
-      selectInput("flatType", "Select Flat Type:", 
-                  choices = c("3 ROOM", "4 ROOM", "5 ROOM", "EXECUTIVE"), # Specify the types you want to include
-                  selected = "3 ROOM",
-                  multiple = TRUE),
-      checkboxGroupInput("year", "Select Year(s):",
-                         choices = c('1990', '2022'),
-                         selected = c('1990', '2022'))
-    ),
-    mainPanel(
-      plotOutput("boxPlot")
-    )
-  )
-)
-
-# Define Server Logic
-server <- function(input, output, session) {
-  # Call the global data combining function
-  combinedData <- combine_data("www/ResaleFlatPrices1999.csv", "www/ResaleFlatPrices2022.csv")
-  
-  # Update the choices for selectInput based on the combined data
-  updateSelectInput(session, "flatType", 
-                    choices = unique(combinedData$flat_type),
-                    selected = unique(combinedData$flat_type)[1])
-  
-  output$boxPlot <- renderPlot({
-    # Filter data based on selected flat type and year(s)
-    filteredData <- filter(combinedData, 
-                           flat_type %in% input$flatType,
-                           Year %in% as.numeric(input$year))
-    
-    # Create box plot
-    ggplot(filteredData, aes(x = flat_type, y = resale_price, fill = as.factor(Year))) +
-      geom_boxplot() +
-      scale_y_continuous(labels = label_dollar()) + # Format the y axis as dollar
-      theme_minimal() +
[…]

### 2023-11-14 datastory.qmd
Project Update

@@
 ### Assessing Affordability of Resale Flats in Singapore
-
+<p style="text-align: justify;">
+So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned.
 ```{r, eval=FALSE,echo=FALSE}
@@
 ### Conclusion
+<p style="text-align: justify;">
+You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right!
+But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
+</p>
 

### 2023-11-14 game.R

@@ -1,0 +1,39 @@
+library(shiny)
+
+# Define UI
+ui <- fluidPage(
+  titlePanel("Find Your Dream HDB Flat"),
+  sidebarLayout(
+    sidebarPanel(
+      numericInput("income", "Your Monthly Income:", value = 4000),
+      numericInput("spouse_income", "Spouse's Monthly Income:", value = 4000),
+      actionButton("calculate", "Calculate Best Option")
+    ),
+    mainPanel(
+      textOutput("recommendation")
+    )
+  )
+)
+
+# Define server logic
+server <- function(input, output) {
+  observeEvent(input$calculate, {
+    # Here you would have the logic to calculate the combined income
+    # and determine which flat types are affordable, then make a recommendation.
+    combined_income <- input$income + input$spouse_income
+    
+    # Stub for recommendation logic
+    recommendation <- ifelse(combined_income > 10000, "5-Room or Executive", 
+                             ifelse(combined_income > 7000, "4-Room", "3-Room"))
+    
+    # Output the recommendation
+    output$recommendation <- renderText({
+      paste("Based on your combined monthly income of $", combined_income,
+            ", we recommend considering a ", recommendation, " HDB flat.", sep = "")
+    })
+  })
+}
+
+# Run the application
+shinyApp(ui = ui, server = server)
+

### 2023-11-14 datastory.qmd
Project Update

--- 2023-11-14 datastory.qmd
@@
 </p>
-
 ![](docs/images/dreamhome.png){fig-align="center" width="698"}
@@
 ```
+<p style="text-align: justify;">
+The interactive graph above compares 
+</p>
 
@@
 <p style="text-align: justify;">
-Hint: Pay attention to how 3-room flats almost hitting $1,000,000!
+Hint: Pay attention to how 3-room flats almost hitting \$1,000,000!
 On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively.
@@
 
+<p style="text-align: justify;">
+So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned.
+</p>
 ```{r, eval=FALSE,echo=FALSE}
@@
 
+<p style="text-align: justify;">
+You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right!
+But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
+</p>
+
+<p style="text-align: justify;">
+
 ```{r, eval=TRUE,echo=FALSE}
@@
 ### References
+
 ```{r}

### 2023-11-14 myapp/app.R

@@ -1,90 +1,0 @@
-library(shiny)
-
-# Define UI for slider demo app ----
-ui <- fluidPage(
-  
-  # App title ----
-  titlePanel("My Shiny App!"),
-  img(src = "face.png", height = 140, width = 140),
-  
-  # Sidebar layout with input and output definitions ----
-  sidebarLayout(
-    
-    # Sidebar to demonstrate various slider options ----
-    sidebarPanel(
-      
-      # Input: Simple integer interval ----
-      sliderInput("integer", "Integer:",
-                  min = 0, max = 1000,
-                  value = 500),
-      
-      # Input: Decimal interval with step value ----
-      sliderInput("decimal", "Decimal:",
-                  min = 0, max = 1,
-                  value = 0.5, step = 0.1),
-      
-      # Input: Specification of range within an interval ----
-      sliderInput("range", "Range:",
-                  min = 1, max = 1000,
-                  value = c(200,500)),
-      
-      # Input: Custom currency format for with basic animation ----
-      sliderInput("format", "Custom Format:",
-                  min = 0, max = 10000,
-                  value = 0, step = 2500,
-                  pre = "$", sep = ",",
-                  animate = TRUE),
-      
-      # Input: Animation with custom interval (in ms) ----
-      # to control speed, plus looping
-      sliderInput("animation", "Looping Animation:",
-                  min = 1, max = 2000,
-                  value = 1, step = 10,
-                  animate =
-                    animationOptions(interval = 300, loop = TRUE))
-      
-    ),
-    
-    # Main panel for displaying outputs ----
-    mainPanel(
-      h1("Hello Everyone!"),
-      h2("I edited this already as my customisation"),
-      h3("I added a photo"),
-      strong("Here is the table:"),
-      # Output: Table summarizing the values entered ----
-      tableOutput("values")
-      
-    )
-  )
-)
-
-# Define server logic for slider examples ----
-server <- function(input, output) {
-  
-  # Reactive expression to create data frame of all input values ----
-  sliderValues <- reactive({
-    
-    data.frame(
-      Name = c("Integer",
-               "Decimal",
-               "Range",
-               "Custom Format",
-               "Animation"),
-      Value = as.character(c(input$integer,
-                             input$decimal,
-                             paste(input$range, collapse = " "),
-                             input$format,
-                             input$animation)),
-      stringsAsFactors = FALSE)
-    
-  })
-  
[…]

### 2023-11-14 datastory.qmd
Project Update

@@
 
-```{r, eval=TRUE,echo=FALSE}
+<iframe height="550" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/bargraph/">
 
-library(ggplot2)
+</iframe>
 
-data <- data.frame(
-  category = c("A", "B", "C", "D"),
-  value = c(23, 45, 12, 78)
-)
-
-ggplot(data, aes(x = category, y = value)) +
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  labs(title = "Simple Bar Graph", x = "Category", y = "Value")
-
-```
 <p style="text-align: justify;">

### 2023-11-14 datastory.qmd
Project Update

@@
 <p style="text-align: justify;">
-For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at lease earn SGD\$5,230.
+For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230.
 While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
@@
 Now let's look at the price increment individually for both years, compared with the same flat type.
+The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
+The year 1990 with an average price of SGD$81,525 and 2022 with an average price of SGD$525,092, represented by green and orange respectively.
+In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022!
 </p>
@@
 <p style="text-align: justify;">
-The interactive graph above compares 
+As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options.
+Additionally, the graph suggests that the real estate market has become increasingly segmented.
+Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020).
+</p>
+
+<p style="text-align: justify;">
+For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019).
+To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market.
 </p>
@@
 
+https://www.todayonline.com/singapore/property-agent-fined-s30000-suspended-12-months-over-unethical-bid-pocket-bigger
+
+https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice
 ```{r}

### 2023-11-15 datastory.qmd
Project Update

@@
 <p style="text-align: justify;">
+
 In Singapore, housing affordability has been an increasing worry for future Singaporeans.
 However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
+
 </p>
@@
 <p style="text-align: justify;">
+
 While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
 This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.
+
 </p>
@@
 <p style="text-align: justify;">
+
 The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
+
 </p>
+
 ![](docs/images/dreamhome.png){fig-align="center" width="698"}
@@
 <p style="text-align: justify;">
+
 According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue.
@@
 Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.
+
 </p>
@@
 <p style="text-align: justify;">
+
 For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230.
 While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Imagine you and your sponse are looking to start a family.
@@
 Let's dive into real data and discuss this critical issue further.
+
 </p>
+
+![](src/images/flats.jpeg)
 
@@
 <p style="text-align: justify;">
+
 To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
 The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Before moving on to the deeper analysis, let us understand how the overall prices have increased from 1990 to 2022.
 While the general increase in prices overtime aligns with economic growth, the rate of the surge from 1990 to 2022 is alarming.
+
 </p>
@@
 <p style="text-align: justify;">
+
 One may argue that the increment is a sign of prospering economy, on the other side, it also rings alarm bells in terms of overall affordability. Now let's examine the graph below:
+
 </p>
@@
 <p style="text-align: justify;">
+
 The graph above illustrates a significant steepening in the slopes of average resale prices in Singapore from 1990 to 2022 - indicating the exorbitant increase of prices across all flat types.
@@
 This is can be an indication increasing pressure on affordability and financial stretch for home ownership.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Notice that on the graph, there is a worrying widening price gap between each successive flat type, with the difference in average prices from one flat type to the next becoming more distinct.
@@
 Larger home, bigger family right?
+
 </p>
@@
 <p style="text-align: justify;">
+
 With that, we can understand that the widening gap of prices could create a cost burden for upgraders seeking more specious accommodations for a bigger family.
 The growing gap in prices shows that planning for home ownership is extremely crucial to prevent any buyers' remorse.
+
 </p>
 
+### Comparing Average Resale Prices of Flat Types by Years
+
 <p style="text-align: justify;">
+
 Now let's look at the price increment individually for both years, compared with the same flat type.
 The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
-The year 1990 with an average price of SGD$81,525 and 2022 with an average price of SGD$525,092, represented by green and orange respectively.
+The year 1990 with an average price of SGD\$81,525 and 2022 with an average price of SGD\$525,092, represented by green and orange respectively.
 In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022!
+
 </p>
@@
 <p style="text-align: justify;">
+
 As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options.
@@
 Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020).
+
 </p>
@@
 <p style="text-align: justify;">
+
 For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019).
 To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market.
+
 </p>
@@
 <p style="text-align: justify;">
+
 While a price increment can potentially indicate a critical issue with affordability, it is also important to access where the increase is still within the "safe" median range.
 However, in the box plot below, we can see how the presence of outliers underscores the significant and unprecedented price increase.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Hint: Pay attention to how 3-room flats almost hitting \$1,000,000!
 On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Let's input all the flat type options, what do you see?
@@
 This inevitably affect those within a lower income bracket, preventing them to do the same.
+
 <p>
@@
 <p style="text-align: justify;">
+
 Furthermore, across the other flat types, there is an increasing number of outliers beyond the upper whiskers of the box plots for 2022.
 While this can suggest a substantial market growth, it can also reflect the high number of exceptional cases where resale prices are charging a even higher premium, exceeding the median trends - which is already high.
+
 </p>
@@
 <p style="text-align: justify;">
+
 Now, that we have clearly seen the high prices Singaporean are willing to pay for their dream home, are there other factors that can be attributed to the price increase?
 Next, we will explore if the remaining lease left or the location of the flat affect the resale price.
+
 </p>
@@
 <p style="text-align: justify;">
+
 To lower the cost burden for flat upgraders, some may consider purchasing a flat with a lower remaining lease.
-However, is there a correlation between the remaining lease and the cost of a resale flat?
+However, is there a correlation between the remaining lease and the cost of a resale flat in 1990 and 2022?
+As we look and examine into the numbers, it becomes clear that patterns have shifted from 1990 to 2022.
+Here, we will be comparing the data from these two distinct years.
+Now let's look at the scatterplot below.
+Pay attention to the red line, what does it tell you?
+
 </p>
 
-```{r, eval=TRUE,echo=FALSE}
+<iframe height="500" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/scatterplot/">
 
-ggplot(mtcars, aes(x = wt, y = mpg)) +
-  geom_point() +
-  labs(title = "Title", 
-       x = "x-axis", 
-       y = "y-axis")
-```
-
-### The influence of Estate on Resale Prices
+</iframe>
 
 <p style="text-align: justify;">
+
+In 1990, the line suggested a clear trend: where a longer remaining lease often correlated with a higher resale price.
+The regression line showed a noticeable upward slope; decently steep actually.
+This would indicate that the longer the remaining lease, the higher the resale price of the flat, which makes sense at the time where buyers could reside in the flat without facing any lease expiration issue in the future.
+
+</p>
+
+<p style="text-align: justify;">
+
+However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep.
+This suggests that the remaining lease period is not as strong an indicator as it was in 1990.
+Also, the data points are more spread out , inidcating a high variance in resale prices.
+We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.
+
+</p>
+
+<p style="text-align: justify;">
+
+![](src/images/buy.jpeg)
+
+Put yourself in the shoes of the buyer, would you get a house with longer remaining lease, but with everything else an hour away or a shorter remaining lease with everything else a stone's throw away?
+The answer is not merely a matter of counting the years on a lease.
+So far, none of the HDB flats have seen their lease expired.
+So no one knows what really happens after that.
+Buying your own home is also about weighing the value or time and quality of your daily life.
+After all, what is a good extended lease if it comes at an expense of your convenience and time?
+Now, we will look into another important factor: The Estate
+
+</p>
+
+### The Influence of Estate on Resale Prices
+
+<p style="text-align: justify;">
+
 We can agree that price is an important consideration for purchasing a home.
@@
 Or do you have a preferred school you would like to send your future children too?
+
 </p>
 
+![](src/images/school.png)
+
 <p style="text-align: justify;">
+
 Now, we will examine if the estate affects the price of the resale flat. We will also determine which estate tends to be more costly or cheaper to settle down.
+
 </p>
 
-```{r, eval=TRUE,echo=FALSE}
-ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
-  geom_violin(trim=FALSE) +
-  labs(title = "TITLE", 
-       x = "x-axis", 
-       y = "y-axis")
+<iframe height="450" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/violin/">
 
-```
+</iframe>
 
@@
 <p style="text-align: justify;">
+
 So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned.
+
 </p>
+
 ```{r, eval=FALSE,echo=FALSE}
@@
 
+### Why such analysis is important?
+
+<p style="text-align: justify;">
+
+Soon, it will be time for the "Gen-Zs" to consider purchasing a new home.
+
+</p>
+
 ### Conclusion
@@
 <p style="text-align: justify;">
+
 You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right!
 But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
+
 </p>
@@
 https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice
+
 ```{r}

### 2023-11-15 datastory.qmd
Project Update

@@
 
-Now let's look at the price increment individually for both years, compared with the same flat type.
-The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
+Now let's look at the price increment individually for both years, compared with the same flat type. The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
+
+</p>
+
+<p style="text-align: justify;">
+
 The year 1990 with an average price of SGD\$81,525 and 2022 with an average price of SGD\$525,092, represented by green and orange respectively.
@@
 
+![](src/images/school.png)
+
 <p style="text-align: justify;">
@@
 Or do you have a preferred school you would like to send your future children too?
-
-</p>
-
-![](src/images/school.png)
-
-<p style="text-align: justify;">
-
-Now, we will examine if the estate affects the price of the resale flat. We will also determine which estate tends to be more costly or cheaper to settle down.
+Now, we will examine if the estate affects the price of the resale flat.
+We will also determine which estate tends to be more costly or cheaper to settle down.
 
@@
 </iframe>
+
+<p style="text-align: justify;">
+
+Now, let's explore the violin plot on the interactive dashboard.
+For visualisation, we will use Bukit Timah and Punggol.
+According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is known for it access to many well sought after educational institutes such as Hwa Chong Institutions, National Junior College and Raffles Girls' Primary School, making it one of the most popular estate.
+[Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate.
+It is slowly becoming popular with younger couples due to its modern amenities and promising development plans.
+The town is being developed with a vision to be eco-friendly, sustainable while providing trendy lifestyle hubs that cater to all age groups.
+
+</p>
+
+<p style="text-align: justify;">
+
+That being said, let's analyse the violin plot.
+We can observe the wider distribution of resale prices, with a more pronounced upper tail.
+This would indicate there are a larger variety of flats, but also a substantial market for high-end luxury flats.
+On the flip side, Punggol has a narrower but dense concentration of price, indicating a more concrete (or less variation) in resale prices.
+Now, let's interact with the plot, select your dream estates and explore the price variations!
+Oh and just in case, 'll put the MRT Map here for reference!
+
+</p>
+
+![](src/images/mrt.avif)
+
+<p style="text-align: justify;">
+
+Now, if we were to deduce on which is the best place to settle down based on what we have gathered, the decision really depends on what you value the most.
+For instance, if you value tranquility and a sea view, Punggol would be great.
+However, if you would like be in close proximity of prestigious schools, *(all schools are good schools - but let's not get into that for now)* then Bukit Timah might be the best choice for you!
+The visualisation does not only tell us about the prices, but also a reflection of lifestyle, and the long-term family vision for you and your spouse!
+
+</p>
 
@@
 
+https://www.99.co/singapore/neighbourhoods/punggol
+
+https://www.99.co/singapore/neighbourhoods/bukit-timah
+
 ```{r}

### 2023-11-15 datastory.qmd
Project Update

@@
 </p>
+
+![](src/images/tharman.webp){width="800"}
 
@@
 
-<iframe height="550" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/bargraph/">
+<iframe height="450" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/bargraph/">
 
@@
 The data reveals a distinct trend where "regular-sized" flats are slowly approaching the million-dollar mark in resale price in 2022.
+
+</p>
+
+<p style="text-align: justify;">
+
 The upward trajectory is also an indication of the growth in the resale market, reflecting how people are willing to pay for their dream home.
@@
 
-<p>
+</p>
+
+![](src/images/darkhome.jpeg)
 
@@
 However, is there a correlation between the remaining lease and the cost of a resale flat in 1990 and 2022?
+
+</p>
+
+<p style="text-align: justify;">
+
 As we look and examine into the numbers, it becomes clear that patterns have shifted from 1990 to 2022.
@@
 Put yourself in the shoes of the buyer, would you get a house with longer remaining lease, but with everything else an hour away or a shorter remaining lease with everything else a stone's throw away?
+
+</p>
+
+<p style="text-align: justify;">
+
 The answer is not merely a matter of counting the years on a lease.
@@
 
-![](src/images/school.png)
+![](src/images/bukitpunggol.png)
 
@@
 According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is known for it access to many well sought after educational institutes such as Hwa Chong Institutions, National Junior College and Raffles Girls' Primary School, making it one of the most popular estate.
+
+</p>
+
+<p style="text-align: justify;">
+
 [Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate.
@@
 This would indicate there are a larger variety of flats, but also a substantial market for high-end luxury flats.
+
+</p>
+
+<p style="text-align: justify;">
+
 On the flip side, Punggol has a narrower but dense concentration of price, indicating a more concrete (or less variation) in resale prices.
 Now, let's interact with the plot, select your dream estates and explore the price variations!
-Oh and just in case, 'll put the MRT Map here for reference!
+Oh and just in case, I'll put the MRT Map here for reference!
 
@@
 For instance, if you value tranquility and a sea view, Punggol would be great.
+
+</p>
+
+<p style="text-align: justify;">
+
 However, if you would like be in close proximity of prestigious schools, *(all schools are good schools - but let's not get into that for now)* then Bukit Timah might be the best choice for you!

### 2023-11-15 datastory.qmd
Project Update

@@
 
-### Assessing Affordability of Resale Flats in Singapore
+### Assessing Affordability of Resale Flats in Singapore for you!
 
@@
 
-So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable for Singaporeans - compared with the average income earned.
+So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable!
+Soon, it will be time for you to consider purchasing a new home so let's play a little game.
 
@@
 
-```{r, eval=FALSE,echo=FALSE}
+<p style="text-align: justify;">
 
-```
+According to YCharts, the 5-year inflation rate tends to be about 2.46%.
+Provided all else remains constant, the calculator would give a rough indication of how much you will have to pay every month to own your dream home - this is inclusive of DBS's 2.6% interest rates.
+The prices you see based on 2022's average cost, and adjusted for inflation in 5 years.
+
+</p>
+
+<iframe height="750" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
+
+</iframe>
 
@@
 <p style="text-align: justify;">
-
-Soon, it will be time for the "Gen-Zs" to consider purchasing a new home.
 
@@
 
+https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:~:text=Basic%20Info,long%20term%20average%20of%202.25%25.
+
+https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.
+
 ```{r}

### 2023-11-15 game.R

@@ -1,39 +1,53 @@
 library(shiny)
+library(dplyr)
+
+# Assuming the flat type and town are in columns named 'flat_type' and 'town', 
+# and the price is in a column named 'resale_price'.
+
+# Read the dataset
+data_2022 <- read.csv("/mnt/data/ResaleFlatPrices2022.csv")
+
+# Pre-calculate the average prices for each flat type and town
+average_prices <- data_2022 %>%
+  group_by(flat_type, town) %>%
+  summarize(average_price = mean(resale_price, na.rm = TRUE))
 
 # Define UI
 ui <- fluidPage(
-  titlePanel("Find Your Dream HDB Flat"),
+  titlePanel("HDB Resale Price Estimator"),
   sidebarLayout(
     sidebarPanel(
-      numericInput("income", "Your Monthly Income:", value = 4000),
-      numericInput("spouse_income", "Spouse's Monthly Income:", value = 4000),
-      actionButton("calculate", "Calculate Best Option")
+      numericInput("income", "Your Annual Income:", value = 50000),
+      numericInput("spouse_income", "Spouse's Annual Income:", value = 50000),
+      selectInput("flat_type", "Preferred Flat Type:", choices = unique(data_2022$flat_type)),
+      selectInput("town", "Preferred Town:", choices = unique(data_2022$town)),
+      actionButton("estimate", "Estimate Price")
     ),
     mainPanel(
-      textOutput("recommendation")
+      verbatimTextOutput("result")
     )
   )
 )
 
 # Define server logic
 server <- function(input, output) {
-  observeEvent(input$calculate, {
-    # Here you would have the logic to calculate the combined income
-    # and determine which flat types are affordable, then make a recommendation.
-    combined_income <- input$income + input$spouse_income
+  
+  observeEvent(input$estimate, {
+    # Filter the pre-calculated average prices based on user selection
+    selected_price <- average_prices %>%
+      filter(flat_type == input$flat_type, town == input$town) %>%
+      .$average_price
     
-    # Stub for recommendation logic
-    recommendation <- ifelse(combined_income > 10000, "5-Room or Executive", 
-                             ifelse(combined_income > 7000, "4-Room", "3-Room"))
-    
-    # Output the recommendation
-    output$recommendation <- renderText({
-      paste("Based on your combined monthly income of $", combined_income,
-            ", we recommend considering a ", recommendation, " HDB flat.", sep = "")
+    # Display the result
+    output$result <- renderText({
[…]

### 2023-11-15 game/game.R

@@ -1,0 +1,70 @@
+library(shiny)
+library(dplyr)
+
+
+data_2022 <- read.csv("www/ResaleFlatPrices2022.csv")
+
+
+average_prices <- data_2022 %>%
+  group_by(flat_type, town) %>%
+  summarize(average_price = mean(resale_price, na.rm = TRUE))
+
+# Define UI
+ui <- fluidPage(
+  titlePanel(""),
+  sidebarLayout(
+    sidebarPanel(
+      numericInput("income", "Your Annual Income in SGD$:", value = 3000),
+      numericInput("spouse_income", "Spouse's Annual Income in SGD$:", value = 3000),
+      selectInput("flat_type", "Preferred Flat Type:", choices = unique(data_2022$flat_type)),
+      selectInput("town", "Preferred Town:", choices = unique(data_2022$town)),
+      numericInput("interest_rate", "Annual Interest Rate (%):", value = 2.6),
+      numericInput("loan_tenure", "Loan Tenure (Years):", value = 25, min = 1, max = 30),
+      actionButton("calculate", "Calculate"),
+      tags$hr(),  # Horizontal line to separate the inputs from the output
+      div(style = "text-align: left;", textOutput("downpayment")), br(),
+      div(style = "text-align: left;", textOutput("monthly_repayment"))
+    ),
+    mainPanel()
+  )
+)
+
+
+# Define server logic
+server <- function(input, output) {
+  
+  observeEvent(input$calculate, {
+    # this basically filters the average price and their towns
+    selected_price <- average_prices %>%
+      filter(flat_type == input$flat_type, town == input$town) %>%
+      .$average_price
+    
+    # multiply to consider inflation
+    inflation_rate <- 0.0246  # 2.46% inflation rate
+    future_price <- selected_price * ((1 + inflation_rate) ^ input$loan_tenure)
+    
+    # calculate downpayment and loan based on the inflated price
+    downpayment <- future_price * 0.2
+    loan_principal <- future_price * 0.8
+    
+    # just show the downpayment
+    output$downpayment <- renderText({
+      paste("Minimum downpayment for a", input$flat_type, "in", input$town, 
+            "with an expected inflation rate is $",round(downpayment, 2))
+    })
+    
+    # this helps to calculate the monthly payment
+    r <- input$interest_rate / 100 / 12  
+    n <- input$loan_tenure * 12  
[…]

### 2023-11-15 datastory.qmd
Project Update

@@
 So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable!
-Soon, it will be time for you to consider purchasing a new home so let's play a little game.
+Soon, it will be time for you to consider purchasing a new home so let's play a little game!
 
@@
 
-<iframe height="750" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
+<iframe height="700" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
 

### 2023-11-23 about.qmd
Project Update

--- 2023-10-19 about.qmd
@@
 ---
-title: "Data Story"
+title: "My Experiences"
 ---
 
-<br>
+![](src/images/aboutme.png)
 
-### Investigating Singapore's Resale Flat Prices from 1990 to 2023
+## My Work and Internship Experience - [My LinkedIn Profile](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
 
-##### Is public housing in Singapore affordable for the average Singaporean?
+**- Specialist**\
+*Apple South Asia* <br> Aug 2023 - Present · 4 mos
 
-<br> This is where my introduction will be. This is just a placeholder for potential data sets!
+**- Galaxy Specialist · Part-time**\
+*Samsung Electronics Singapore* <br>Feb 2018 - Jan 2023 · 5 yrs
 
-```{r, eval=TRUE,echo=FALSE}
-library(tidyverse)
-starwars
-```
+**- Business Information Technology Interest Group - Honorary Secretary**\
+*Temasek Polytechnic* <br>Apr 2019 - Apr 2021 · 2 yrs 1 mo
+
+**- Application Development Intern**\
+*Accenture · Internship* <br>Apr 2020 - Aug 2020 · 5 mos
+
+**- Marketing Research Intern**\
+*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos
+
+**- Instructor**\
+*Singapore Civil Defence Force · Full-time* <br>Feb 2016 - Nov 2017 · 1 yr 10 mos
+
+**- Attraction Host Lead**\
+*Sentosa Development Corporation · Part-time* <br>Oct 2013 - Nov 2015 · 2 yrs 2 mos

### 2023-11-23 index.qmd
update
Project Update

@@
 ---
-title: "Marzuki Nooranas"
+title: "Well Hello There!"
 ---
@@
 
-### [Link to Course Content from Week 1 to Week 9](https://github.com/mrzknrns/mrzknrns.git){.uri}
-
-```{r, eval=TRUE,echo=FALSE}
-
-library(grid)
-library(gridExtra)
-library(png)
-
-img1 <- readPNG("src/images/me_icon.png")
-img2 <- readPNG("src/images/68FD47AF-F084-4FCC-85AC-4712EEC1B685.PNG")
-
-grid.arrange(rasterGrob(img1, width=unit(1.1,"npc"), height=unit(0.8,"npc"), gp=gpar(mai=c(0,0,0,0))), 
-             rasterGrob(img2, width=unit(1,"npc"), height=unit(0.7,"npc"), gp=gpar(mai=c(0,0,0,0))), 
-             ncol=2)
-
-```
+![](src/images/namelogo.png){fig-align="left" width="724"}
 
 # **My Hello to You \~**
+
+![](src/images/me2.jpg)
 
@@
 
+### SC3101 - Social Thought and Theory
+
+In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
+This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
+
+This idea that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
+How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
+
+{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
+
+### HS1501 - Artificial Intelligence and Society
+
+In this module, we looked at the benefits and potential downsides of relying on AI.
+My group focused on leveraging on AI technology to aid in bereavement process.
+I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with thier loved ones - as an avatar!
+
+![](docs/src/images/brochure.png)
+
 ### DTK1234 - Design Thinking
@@
 
-#
-
 ```         

### 2023-11-23 about.qmd
Weekly Update

--- 2023-10-19 about.qmd
@@
 ---
-title: "Data Story"
+title: "My Experiences"
 ---
 
-<br>
+![](src/images/aboutme.png)
 
-### Investigating Singapore's Resale Flat Prices from 1990 to 2023
+## Education
+**National University of Singapore**\
+*Bachelor of Social Sciences [Hons.], Communications New Media / Sociology, Social Sciences*
+<br> Aug 2022 - Present
 
-##### Is public housing in Singapore affordable for the average Singaporean?
+**Temasek Polytechnic**\
+*Diploma with Merit, Business Information Technology*
+<br> Apr 2018 - Apr 2021
 
-<br> This is where my introduction will be. This is just a placeholder for potential data sets!
+**ITE College Central**\
+*Higher Nitec in Business Event Management*
+<br> Apr 2013 - Apr 2015
 
-```{r, eval=TRUE,echo=FALSE}
-library(tidyverse)
-starwars
-```
+## Work and Internship Experience - [My LinkedIn Profile](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
+
+**Product Specialist**\
+*Apple South Asia* <br> Aug 2023 - Present · 4 mos
+
+**Galaxy Specialist · Part-time**\
+*Samsung Electronics Singapore* <br>Feb 2018 - Jan 2023 · 5 yrs
+
+**Business Information Technology Interest Group - Honorary Secretary**\
+*Temasek Polytechnic* <br>Apr 2019 - Apr 2021 · 2 yrs 1 mo
+
+**Application Development Intern**\
+*Accenture · Internship* <br>Apr 2020 - Aug 2020 · 5 mos
+
+**Marketing Research Intern**\
+*Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos
+
+**Instructor**\
+*Singapore Civil Defence Force · Full-time* <br>Feb 2016 - Nov 2017 · 1 yr 10 mos
+
+**Attraction Host Lead**\
+*Sentosa Development Corporation · Part-time* <br>Oct 2013 - Nov 2015 · 2 yrs 2 mos

### 2023-11-23 datastory.qmd
Weekly Update

@@
 
-https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:~:text=Basic%20Info,long%20term%20average%20of%202.25%25.
+https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:\~:text=Basic%20Info,long%20term%20average%20of%202.25%25.
 
-https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.
+https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:\~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.
 

### 2023-11-23 datastory.qmd
Project Update

--- 2023-11-15 datastory.qmd
@@
 
-<iframe height="700" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
-
-</iframe>
+<div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
+  <iframe height="800" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
+</div>
 
@@
 
+Year-on-year, the prices of resale HDB flats have seen a continuous rise, reflecting in a growing demand of housing solutions in Singapore.
+However, this brings concerns to many Singaporeans, especially younger couples intending to start a family, as they struggle with affordability and availability issues.
+
 </p>
 
-### Conclusion
+<p style="text-align: justify;">
+
+According to recent reports, analysts indicated that prices of resale flats are expected to rise moderately for the remainder of 2023 (CNA, 2023).
+While cooling measures have taken place to control the prices, the growth in the third quarter of 2023 was due to price resistance setting in amid inflationary and affordability concerns.
+
+</p>
 
@@
 But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
+Certainly, the choice to ballot for a BTO flat, despite its lower cost and readily available grants, requires risk-taking and uncertainties.
 
@@
 <p style="text-align: justify;">
+
+Therefore, this analysis could provide a thoughtful evaluation of the need for immediate housing against the potential delays and challenges of the BTO process.
+For now, all we can do is leverage on the available grants and ensure that we spend on what we can afford.
 
@@
 
-https://www.todayonline.com/singapore/property-agent-fined-s30000-suspended-12-months-over-unethical-bid-pocket-bigger
-
-https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice
-
-https://www.99.co/singapore/neighbourhoods/punggol
-
-https://www.99.co/singapore/neighbourhoods/bukit-timah
-
-https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate#:~:text=Basic%20Info,long%20term%20average%20of%202.25%25.
-
-https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans#:~:text=With%20HDB%20loans%2C%20the%20interest,has%20not%20changed%20in%20years.
-
 ```{r}

### 2023-11-23 game/game.R

@@ -1,9 +1,7 @@
 library(shiny)
 library(dplyr)
 
-
 data_2022 <- read.csv("www/ResaleFlatPrices2022.csv")
-
 
 average_prices <- data_2022 %>%
   group_by(flat_type, town) %>%
@@ -14,8 +12,8 @@ ui <- fluidPage(
   titlePanel(""),
   sidebarLayout(
     sidebarPanel(
-      numericInput("income", "Your Annual Income in SGD$:", value = 3000),
-      numericInput("spouse_income", "Spouse's Annual Income in SGD$:", value = 3000),
+      numericInput("income", "Your Total Annual Income in SGD$:", value = 50000),
+      numericInput("spouse_income", "Spouse's Total Annual Income in SGD$:", value = 50000),
       selectInput("flat_type", "Preferred Flat Type:", choices = unique(data_2022$flat_type)),
       selectInput("town", "Preferred Town:", choices = unique(data_2022$town)),
       numericInput("interest_rate", "Annual Interest Rate (%):", value = 2.6),
@@ -23,48 +21,63 @@ ui <- fluidPage(
       actionButton("calculate", "Calculate"),
       tags$hr(),  # Horizontal line to separate the inputs from the output
       div(style = "text-align: left;", textOutput("downpayment")), br(),
-      div(style = "text-align: left;", textOutput("monthly_repayment"))
+      div(style = "text-align: left;", textOutput("monthly_repayment")), br(),
+      div(style = "text-align: left;", textOutput("advice"))
     ),
     mainPanel()
   )
 )
 
-
 # Define server logic
 server <- function(input, output) {
   
-  observeEvent(input$calculate, {
-    # this basically filters the average price and their towns
+  # eventReactive for calculate button - this basically consistantly watches the input from the user. 
+  result <- eventReactive(input$calculate, {
     selected_price <- average_prices %>%
       filter(flat_type == input$flat_type, town == input$town) %>%
       .$average_price
     
-    # multiply to consider inflation
     inflation_rate <- 0.0246  # 2.46% inflation rate
     future_price <- selected_price * ((1 + inflation_rate) ^ input$loan_tenure)
     
-    # calculate downpayment and loan based on the inflated price
     downpayment <- future_price * 0.2
     loan_principal <- future_price * 0.8
     
-    # just show the downpayment
+    r <- input$interest_rate / 100 / 12
+    n <- input$loan_tenure * 12
+    monthly_repayment <- loan_principal * (r * (1 + r)^n) / ((1 + r)^n - 1)
+    
[…]

### 2023-11-23 datastory.qmd
Project Update

@@
 <div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
-  <iframe height="800" width="150%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
+  <iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
 </div>

### 2023-11-23 datastory.qmd
Project Update

@@
 
-For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230.
+For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD$5,230.
 While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
@@
 This suggests that the remaining lease period is not as strong an indicator as it was in 1990.
-Also, the data points are more spread out , inidcating a high variance in resale prices.
+Also, the data points are more spread out , indicating a high variance in resale prices.
 We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.
@@
 
+<p style="text-align: justify; font-size: smaller;">
+Bukit Timah Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/bukit-timah
+
+DBS Singapore. (2023, October 10). What you need to know before getting a home loan | DBS Singapore. DBS. https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans.
+
+CNA.
+(2023, October 2).
+HDB resale prices may keep rising moderately for rest of 2023: Analysts.
+CNA.
+https://www.channelnewsasia.com/singapore/hdb-resale-prices-q3-increase-moderate-supply-bto-2023-analysts-3813581
+
+Household income - latest data. (n.d.-b). Base. https://www.singstat.gov.sg/find-data/search-by-theme/households/household-income/latest-data
+
+Koh, J. (2023, November 19). Is the HDB Resale Flat Market Still Overheating? Seedly. https://blog.seedly.sg/hdb-resale-flats-price-high/
+
+Kumar, S.
+(2022, April 11).
+Here’s The Salary You Need To Earn To Afford These Homes In Singapore [2022 Edition].
+DollarsAndSense.sg.
+https://dollarsandsense.sg/salary-need-earn-afford-homes-singapore/
+
+Liew, I.
+(2023, October 2).
+HDB resale prices up 1.2% in Q3, lower than quarter average in 2022; more flats sold.
+The Straits Times.
+https://www.straitstimes.com/singapore/housing/hdb-resale-prices-up-12-in-q3-lower-than-quarter-average-in-2022-more-flats-sold
+
+Liew, I.
+(2023b, October 1).
+About 1,900 BTO flats in 2 Choa Chu Kang projects to be offered in early Oct launch.
+The Straits Times.
+https://www.straitstimes.com/singapore/housing/about-1900-bto-flats-in-2-choa-chu-kang-projects-to-be-offered-in-early-oct-launch
+
+Lam, F.
+(2020, October 23).
+Singapore property agents urged to be ethical, give accurate advice.
+The Business Times.
+https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice
+
+Lim, K.
+(2019, October 21).
+Property agent fined S$30,000, suspended 12 months over unethical bid to pocket bigger commission.
+TODAY.
+https://www.todayonline.com/singapore/property-agent-fined-s30000-suspended-12-months-over-unethical-bid-pocket-bigger
+
+Tan, J.
+(2012, March 2).
+Online uproar over DPM Tharman’s ‘$1k flat’ statement.
+Yahoo Singapore.
+https://sg.news.yahoo.com/blogs/singaporescene/online-uproar-over-dpm-tharman-1k-flat-statement-132522414.html
+
+Punggol Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/punggol
+
+YCharts. (n.d.). 5-Year, 5-Year forward inflation expectation rate. https://ycharts.com/indicators/5year_5year_forward_inflation_expectation_rate
+
+<p>
+
 ```{r}

### 2023-11-24 about.qmd
Project Update

@@
 ## Education
+
 **National University of Singapore**\
-*Bachelor of Social Sciences [Hons.], Communications New Media / Sociology, Social Sciences*
-<br> Aug 2022 - Present
+*Bachelor of Social Sciences \[Hons.\], Communications New Media / Sociology, Social Sciences* <br> Aug 2022 - Present
 
 **Temasek Polytechnic**\
-*Diploma with Merit, Business Information Technology*
-<br> Apr 2018 - Apr 2021
+*Diploma with Merit, Business Information Technology* <br> Apr 2018 - Apr 2021
 
 **ITE College Central**\
-*Higher Nitec in Business Event Management*
-<br> Apr 2013 - Apr 2015
+*Higher Nitec in Business Event Management* <br> Apr 2013 - Apr 2015
 
-## Work and Internship Experience - [My LinkedIn Profile](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
+## Work & Internship - [LinkedIn Page](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
 

### 2023-11-24 datastory.qmd
Project Update

@@
 <p style="text-align: justify;">
-
 In Singapore, housing affordability has been an increasing worry for future Singaporeans.
 However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
-
 </p>
@@
 <p style="text-align: justify;">
-
 While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
 This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.
-
 </p>
@@
 <p style="text-align: justify;">
-
 The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
-
 </p>
@@
 <p style="text-align: justify;">
-
 According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue.
-The table below provides an outline of the housing prices in Singapore.
+The table above provides an outline of the housing prices in Singapore.
 Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.
-
 </p>
@@
 <p style="text-align: justify;">
-
-For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD$5,230.
+For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230.
 While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Imagine you and your sponse are looking to start a family.
@@
 Let's dive into real data and discuss this critical issue further.
-
 </p>
@@
 <p style="text-align: justify;">
-
 To understand the trend of housing prices in Singapore, the analysis will use the available data sets from [this site](www.data.gov.sg).
 The publicly available data contains historical sales figures on yearly bases, and can be used to access market dynamics and predict future trend.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Before moving on to the deeper analysis, let us understand how the overall prices have increased from 1990 to 2022.
 While the general increase in prices overtime aligns with economic growth, the rate of the surge from 1990 to 2022 is alarming.
-
 </p>
@@
 <p style="text-align: justify;">
-
 One may argue that the increment is a sign of prospering economy, on the other side, it also rings alarm bells in terms of overall affordability. Now let's examine the graph below:
-
 </p>
@@
 <p style="text-align: justify;">
-
 The graph above illustrates a significant steepening in the slopes of average resale prices in Singapore from 1990 to 2022 - indicating the exorbitant increase of prices across all flat types.
@@
 This is can be an indication increasing pressure on affordability and financial stretch for home ownership.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Notice that on the graph, there is a worrying widening price gap between each successive flat type, with the difference in average prices from one flat type to the next becoming more distinct.
@@
 Larger home, bigger family right?
-
 </p>
@@
 <p style="text-align: justify;">
-
 With that, we can understand that the widening gap of prices could create a cost burden for upgraders seeking more specious accommodations for a bigger family.
 The growing gap in prices shows that planning for home ownership is extremely crucial to prevent any buyers' remorse.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now let's look at the price increment individually for both years, compared with the same flat type. The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
-
 </p>
@@
 <p style="text-align: justify;">
-
 The year 1990 with an average price of SGD\$81,525 and 2022 with an average price of SGD\$525,092, represented by green and orange respectively.
 In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022!
-
 </p>
@@
 <p style="text-align: justify;">
-
 As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options.
@@
 Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020).
-
 </p>
@@
 <p style="text-align: justify;">
-
 For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019).
 To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market.
-
 </p>
@@
 <p style="text-align: justify;">
-
 While a price increment can potentially indicate a critical issue with affordability, it is also important to access where the increase is still within the "safe" median range.
 However, in the box plot below, we can see how the presence of outliers underscores the significant and unprecedented price increase.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Hint: Pay attention to how 3-room flats almost hitting \$1,000,000!
 On top of that, we can also visually compare the number of outliers in 1990 and 2022, denoted by the green and orange box respectively.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Let's input all the flat type options, what do you see?
@@
 The data reveals a distinct trend where "regular-sized" flats are slowly approaching the million-dollar mark in resale price in 2022.
-
 </p>
@@
 <p style="text-align: justify;">
-
 The upward trajectory is also an indication of the growth in the resale market, reflecting how people are willing to pay for their dream home.
 This inevitably affect those within a lower income bracket, preventing them to do the same.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Furthermore, across the other flat types, there is an increasing number of outliers beyond the upper whiskers of the box plots for 2022.
 While this can suggest a substantial market growth, it can also reflect the high number of exceptional cases where resale prices are charging a even higher premium, exceeding the median trends - which is already high.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now, that we have clearly seen the high prices Singaporean are willing to pay for their dream home, are there other factors that can be attributed to the price increase?
 Next, we will explore if the remaining lease left or the location of the flat affect the resale price.
-
 </p>
@@
 <p style="text-align: justify;">
-
 To lower the cost burden for flat upgraders, some may consider purchasing a flat with a lower remaining lease.
 However, is there a correlation between the remaining lease and the cost of a resale flat in 1990 and 2022?
-
 </p>
@@
 <p style="text-align: justify;">
-
 As we look and examine into the numbers, it becomes clear that patterns have shifted from 1990 to 2022.
@@
 Pay attention to the red line, what does it tell you?
-
 </p>
@@
 <p style="text-align: justify;">
-
 In 1990, the line suggested a clear trend: where a longer remaining lease often correlated with a higher resale price.
@@
 This would indicate that the longer the remaining lease, the higher the resale price of the flat, which makes sense at the time where buyers could reside in the flat without facing any lease expiration issue in the future.
-
 </p>
@@
 <p style="text-align: justify;">
-
 However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep.
@@
 We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.
-
 </p>
@@
 <p style="text-align: justify;">
-
 ![](src/images/buy.jpeg)
@@
 Put yourself in the shoes of the buyer, would you get a house with longer remaining lease, but with everything else an hour away or a shorter remaining lease with everything else a stone's throw away?
-
 </p>
@@
 <p style="text-align: justify;">
-
 The answer is not merely a matter of counting the years on a lease.
@@
 Now, we will look into another important factor: The Estate
-
 </p>
@@
 <p style="text-align: justify;">
-
 We can agree that price is an important consideration for purchasing a home.
@@
 We will also determine which estate tends to be more costly or cheaper to settle down.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now, let's explore the violin plot on the interactive dashboard.
@@
 According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is known for it access to many well sought after educational institutes such as Hwa Chong Institutions, National Junior College and Raffles Girls' Primary School, making it one of the most popular estate.
-
 </p>
@@
 <p style="text-align: justify;">
-
 [Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate.
@@
 The town is being developed with a vision to be eco-friendly, sustainable while providing trendy lifestyle hubs that cater to all age groups.
-
 </p>
@@
 <p style="text-align: justify;">
-
 That being said, let's analyse the violin plot.
@@
 This would indicate there are a larger variety of flats, but also a substantial market for high-end luxury flats.
-
 </p>
@@
 <p style="text-align: justify;">
-
 On the flip side, Punggol has a narrower but dense concentration of price, indicating a more concrete (or less variation) in resale prices.
@@
 Oh and just in case, I'll put the MRT Map here for reference!
-
 </p>
@@
 <p style="text-align: justify;">
-
 Now, if we were to deduce on which is the best place to settle down based on what we have gathered, the decision really depends on what you value the most.
 For instance, if you value tranquility and a sea view, Punggol would be great.
-
 </p>
@@
 <p style="text-align: justify;">
-
 However, if you would like be in close proximity of prestigious schools, *(all schools are good schools - but let's not get into that for now)* then Bukit Timah might be the best choice for you!
 The visualisation does not only tell us about the prices, but also a reflection of lifestyle, and the long-term family vision for you and your spouse!
-
 </p>
@@
 <p style="text-align: justify;">
-
 So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable!
 Soon, it will be time for you to consider purchasing a new home so let's play a little game!
-
 </p>
@@
 <p style="text-align: justify;">
-
 According to YCharts, the 5-year inflation rate tends to be about 2.46%.
@@
 The prices you see based on 2022's average cost, and adjusted for inflation in 5 years.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Year-on-year, the prices of resale HDB flats have seen a continuous rise, reflecting in a growing demand of housing solutions in Singapore.
 However, this brings concerns to many Singaporeans, especially younger couples intending to start a family, as they struggle with affordability and availability issues.
-
 </p>
@@
 <p style="text-align: justify;">
-
 According to recent reports, analysts indicated that prices of resale flats are expected to rise moderately for the remainder of 2023 (CNA, 2023).
 While cooling measures have taken place to control the prices, the growth in the third quarter of 2023 was due to price resistance setting in amid inflationary and affordability concerns.
-
 </p>
@@
 <p style="text-align: justify;">
-
 You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right!
@@
 Certainly, the choice to ballot for a BTO flat, despite its lower cost and readily available grants, requires risk-taking and uncertainties.
-
 </p>
@@
 <p style="text-align: justify;">
-
 Therefore, this analysis could provide a thoughtful evaluation of the need for immediate housing against the potential delays and challenges of the BTO process.
 For now, all we can do is leverage on the available grants and ensure that we spend on what we can afford.
+</p>
 
@@
 <p style="text-align: justify; font-size: smaller;">
-Bukit Timah Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/bukit-timah
 
-DBS Singapore. (2023, October 10). What you need to know before getting a home loan | DBS Singapore. DBS. https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans.
+Bukit Timah Singapore - latest guide and real estate information, places of interest & things to do \| 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/bukit-timah
+
+DBS Singapore. (2023, October 10). What you need to know before getting a home loan \| DBS Singapore. DBS. https://www.dbs.com.sg/personal/articles/nav/my-home/all-about-home-loans.
 
@@
 (2022, April 11).
-Here’s The Salary You Need To Earn To Afford These Homes In Singapore [2022 Edition].
+Here's The Salary You Need To Earn To Afford These Homes In Singapore \[2022 Edition\].
 DollarsAndSense.sg.
@@
 (2019, October 21).
-Property agent fined S$30,000, suspended 12 months over unethical bid to pocket bigger commission.
+Property agent fined S\$30,000, suspended 12 months over unethical bid to pocket bigger commission.
 TODAY.
@@
 (2012, March 2).
-Online uproar over DPM Tharman’s ‘$1k flat’ statement.
+Online uproar over DPM Tharman's '\$1k flat' statement.
 Yahoo Singapore.
@@
 
-Punggol Singapore - latest guide and real estate information, places of interest & things to do | 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/punggol
+Punggol Singapore - latest guide and real estate information, places of interest & things to do \| 99.co. (n.d.). https://www.99.co/singapore/neighbourhoods/punggol
 

### 2023-11-24 index.qmd
Weekly Update
Project Update

@@
 
-![](src/images/namelogo.png){fig-align="left" width="724"}
-
-# **My Hello to You \~**
+![](src/images/namelogo.png){fig-align="left" width="800"}
 
@@
 
-Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 2nd year, double majoring in Sociology and, Communications and New Media!
+## My Hello to You \~
+
+Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 2nd year, double majoring in Sociology and Communications & New Media!
 
@@
 
-This idea that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
+Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
 How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
@@
 My group focused on leveraging on AI technology to aid in bereavement process.
-I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with thier loved ones - as an avatar!
+I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with their loved ones - as an avatar!
 
@@
 In this module, we were assigned the task of innovating everyday chores.
-Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe
+Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe!
 
@@
 
+Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms!
+
 ```         
 ```
+
+![](src/images/footer.png)

### 2023-12-11 datastory.qmd
Update

--- 2023-11-23 datastory.qmd
@@
 According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue.
-The table below provides an outline of the housing prices in Singapore.
+The table above provides an outline of the housing prices in Singapore.
 Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.
@@
 
-<div style="display: flex; justify-content: center; align-items: center; overflow: hidden;">
-  <iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/"></iframe>
-</div>
+::: {style="display: flex; justify-content: center; align-items: center; overflow: hidden;"}
+<iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
+</iframe>
+:::
 
-### Why such analysis is important?
+### Conclusion: Why such analysis is important?
 
@@
 
+</p>
+
 ```{r, eval=TRUE,echo=FALSE}
@@
 
-### References
+<p>
 

### 2024-04-09 datastory.qmd
Update

@@
 
-### Assessing Affordability of Resale Flats in Singapore for you!
-
-<p style="text-align: justify;">
-
-So far, we have looked at the prices of the resale flats, factors such as remaining lease and estate, we will now access if the resale flats are truly affordable!
-Soon, it will be time for you to consider purchasing a new home so let's play a little game!
-
-</p>
-
-<p style="text-align: justify;">
-
-According to YCharts, the 5-year inflation rate tends to be about 2.46%.
-Provided all else remains constant, the calculator would give a rough indication of how much you will have to pay every month to own your dream home - this is inclusive of DBS's 2.6% interest rates.
-The prices you see based on 2022's average cost, and adjusted for inflation in 5 years.
-
-</p>
-
-::: {style="display: flex; justify-content: center; align-items: center; overflow: hidden;"}
-<iframe height="930" width="100%" frameborder="no" src="https://mrzknrns.shinyapps.io/game/">
-</iframe>
-:::
-
 ### Conclusion: Why such analysis is important?

### 2024-05-09 articles.qmd
Update

--- 2024-04-09 datastory.qmd
@@
 ---
-title: "Singapore's Public Housing Affordability"
+title: "Personal Research and Articles"
 ---
+
+![](docs/src/images/research.jpeg)
+
+Here, I have undertaken multiple personal research projects based on my interests.
+While these initiatives are just for my own skill enhancement, they reflect my commitment to continuously improving my data analysis capabilities.
+Through these projects, I delve into various datasets, exploring patterns and extracting actionable insights.
+<br> <br> This portfolio showcases my journey, illustrating not only my technical skills but also my curiosity and dedication to leveraging data in meaningful ways.
+Each project here is a step towards mastering the art of transforming raw data into compelling narratives and informed decisions.
+Happy reading!
+
+<details>
+
+<summary> Singapore's Public Housing Affordability <br> <p style="text-align: justify;">
+
+In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
+Read more here...
+
+</p>
+
+</summary>
+
+## Is Public Housing Affordable for Singaporeans?
+<p style="text-align: right;">  Monday, 6 Nov 2023 </p>
 
@@
 
-## Is Public Housing Affordable for Singaporeans?
-
 ### Investigating Singapore's Resale Flat Prices from 1990 to 2022
-
-<p style="text-align: justify;">
-
-In Singapore, housing affordability has been an increasing worry for future Singaporeans.
-However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
-
-</p>
 
@@
 ```
+
+</details>
+
+<details>
+
+<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <p style="text-align: justify;">
+
+This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
+Read more here...
+
+</p>
+
+</summary>
+
+## Who Determines Deviant Behaviour?
+
+<p style="text-align: right;">  Friday, 10 May 2024 </p>
+
+![](docs/src/images/school.avif)
+
+<p style="text-align: right;">
+    Photo Source: CNA
+</p>
+The findings emphasize the detrimental effects of punitive measures and highlight the need for supportive reintegration strategies.
+This case underscores the broader implications for educational policy and practices in managing deviance constructively.
+
+### Background
+![](docs/src/images/soon.avif){width="730"}
+
+</details>

### 2024-05-09 interests.qmd
Update

---
title: "My Interests"
---

![](docs/src/images/soon.avif){width="730"}

### 2024-05-09 index.qmd
Update
Update index.qmd

@@
 
-Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 2nd year, double majoring in Sociology and Communications & New Media!
+Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 3rd year, double majoring in Sociology and Communications & New Media!
 
@@
 
-### SC3101 - Social Thought and Theory
+### Social Thought and Theory
 
@@
 
-### HS1501 - Artificial Intelligence and Society
+### Artificial Intelligence and Society
 
@@
 
-### DTK1234 - Design Thinking
+### Design Thinking
 
@@
 
-Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms!
+Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms
 

### 2024-05-09 articles.qmd
Update

@@
 ## Is Public Housing Affordable for Singaporeans?
+
 <p style="text-align: right;"> Monday, 6 Nov 2023 </p>
@@
 
-<p style="text-align: right;">
-    Photo Source: CNA
-</p>
+<p style="text-align: right;"> Photo Source: CNA </p>
+
 The findings emphasize the detrimental effects of punitive measures and highlight the need for supportive reintegration strategies.
@@
 ### Background
-![](docs/src/images/soon.avif){width="730"}
+
+<p> In the heart of Singapore's rigorous educational landscape, shaped by the Compulsory Education Act of 2000, every child is promised a solid 10-year foundational education.
+But beneath these statistics lies the personal struggle of students like Jeremy, whose life challenges disrupt the ideal path set before them.
+
+### The Story of Jeremy
+
+![](docs/src/images/study.png)
+
+<p> "School was my second home until it wasn't," Jeremy recalls, his journey from a model student to a labeled 'truant' marked by circumstances beyond his control.
+When his father fell ill, the burden of financial support fell on his shoulders, forcing him to balance part-time jobs with his studies.
+This new responsibility led to tardiness and eventually, absences, which didn't go unnoticed.
+"I wasn't just late; I was struggling to keep my life together," Jeremy shares.</p>
+
+### The Spiral of Deviance
+
+<p> Jeremy's initial minor infractions soon snowballed into more significant absences.
+"Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains.
+The school's response was punitive---detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant.
+"You're marked, and that marking changes how everyone sees you," he reflects.</p>
+
+### Labeling and Its Impacts
+
+<p> The transformation in how Jeremy was perceived and treated is a classic example of labeling theory in action.
+"Once labeled, you're playing a part scripted for you by those labels," Jeremy says.
+This script was reinforced continually by the detentions and the reactions of his teachers and peers.
+"When you hear 'Wah, bro finally showed up?' enough times, you start to wonder if trying is worth it," he admits.
+
+### Breaking Free
+
+<p> The turning point came with the passing of his father.
+This profound loss forced Jeremy to reassess his life's direction.
+"It made me realize the shortness of life and the long-term consequences of my choices," he states.
+Motivated by his father's memory and the need to support his family, Jeremy began to shed his truant identity.
+"I was more than my circumstances," he asserts.</p>
+
+### Insights from Educators
+
+<p> Educators like Mrs.
+Tan, Jeremy's guidance counselor, emphasize the importance of understanding each student's context.
+"We need to look beyond the behavior to the person behind it.
+Only then can we truly help," she notes.
+Mrs.
+Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around."</p>
+
+### Conclusion
+
+<p> Jeremy's narrative is a reminder of the complexity of deviance within Singapore's educational system.
+His experiences underscore the critical need for educational policies that foster understanding and provide genuine support.
+As Jeremy continues his journey, now a student at a university in Singapore, his story offers hope and a call to action for all involved in shaping young lives.
+"Change starts when we choose to see the person, not just the problem," Jeremy concludes.</p>
 

### 2024-05-09 articles.qmd
Update
Update

@@
 Mrs.
-Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around."</p>
+Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around." </p>
 

### 2024-05-15 articles.qmd
Update

@@
 "Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains.
-The school's response was punitive---detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant.
+The school's response was punitive - detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant.
 "You're marked, and that marking changes how everyone sees you," he reflects.</p>
@@
 </details>
+
+<details>
+
+<summary> Article 3 <br> <p style="text-align: justify;">
+
+</p>
+
+</summary>
+
+## Under Construction
+
+<p style="text-align: right;"> Monday, 6 Nov 2023 </p>
+
+![](docs/src/images/soon.avif){width="730"}
+
+</details>

### 2024-05-28 index.qmd
Update

@@
 
-## My Hello to You \~
+## My Hello to You \~~
 
@@
 
-![](docs/src/images/brochure.png)
+<div style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;">
+  <iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;"
+    src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
+  </iframe>
+</div>
+
+<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> Virtual Memory Garden </a>
 

### 2024-05-28 articles.qmd
Update
Update articles.qmd

@@
 While these initiatives are just for my own skill enhancement, they reflect my commitment to continuously improving my data analysis capabilities.
-Through these projects, I delve into various datasets, exploring patterns and extracting actionable insights.
+Through these projects, I looked into various datasets, exploring patterns and extracting actionable insights.
 <br> <br> This portfolio showcases my journey, illustrating not only my technical skills but also my curiosity and dedication to leveraging data in meaningful ways.
-Each project here is a step towards mastering the art of transforming raw data into compelling narratives and informed decisions.
 Happy reading!
@@
 <details>
-
-<summary> Article 3 <br> <p style="text-align: justify;">
-
-</p>
-
-</summary>
+<summary> Article 3 <br> <p style="text-align: justify;"></p></summary>
 

### 2024-06-19 articles.qmd
Update

@@
 
-<summary> Singapore's Public Housing Affordability <br> <p style="text-align: justify;">
-
-In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+<summary> Singapore's Public Housing Affordability <br> <br>  <p style="text-align: justify;"> In Singapore, housing affordability has been an increasing worry for future Singaporeans.
 However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
 Read more here...
-
-</p>
-
-</summary>
+</p> </summary>
 
@@
 
-<p style="text-align: right;"> Monday, 6 Nov 2023 </p>
+<p style="text-align: right;">
+
+Monday, 6 Nov 2023
+
+</p>
 
@@
 
-<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <p style="text-align: justify;">
-
-This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
+<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p style="text-align: justify;"> This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
 Read more here...
-
-</p>
-
-</summary>
+</p> </summary>
 
@@
 
-<p style="text-align: right;"> Friday, 10 May 2024 </p>
+<p style="text-align: right;"> Friday, 10 May 2024</p>
 
@@
 
-<p style="text-align: right;"> Photo Source: CNA </p>
+<p style="text-align: right;">
+
+Photo Source: CNA
+
+</p>
 
@@
 
-<p> In the heart of Singapore's rigorous educational landscape, shaped by the Compulsory Education Act of 2000, every child is promised a solid 10-year foundational education.
+<p>
+
+In the heart of Singapore's rigorous educational landscape, shaped by the Compulsory Education Act of 2000, every child is promised a solid 10-year foundational education.
 But beneath these statistics lies the personal struggle of students like Jeremy, whose life challenges disrupt the ideal path set before them.
@@
 
-<p> "School was my second home until it wasn't," Jeremy recalls, his journey from a model student to a labeled 'truant' marked by circumstances beyond his control.
+<p>"School was my second home until it wasn't," Jeremy recalls, his journey from a model student to a labeled 'truant' marked by circumstances beyond his control.
 When his father fell ill, the burden of financial support fell on his shoulders, forcing him to balance part-time jobs with his studies.
@@
 
-### The Spiral of Deviance
+### Introduction
 
-<p> Jeremy's initial minor infractions soon snowballed into more significant absences.
-"Each late coming wasn't just about not making it on time; it was about not making it at all," Jeremy explains.
-The school's response was punitive - detentions that isolated him from his peers and classes, embedding him deeper into the role of a truant.
-"You're marked, and that marking changes how everyone sees you," he reflects.</p>
+<p>The Compulsory Education Act of 2000 (Singapore Statues Online, 2024) is a legal framework that ensures every child born after 1996 receives fundamental 10-year educational experiences, helping to develop a strong foundation in literacy, communication skills, and other moral values (MOE, 2023).</p>
 
-### Labeling and Its Impacts
+<p>In 2022, the Ministry of Education's (MOE) Education Statistic Digest reported that 235,116 children were enrolled on a Primary School and more than 98% of the Primary Six cohort were eligible for Secondary School education.
+Therefore, missing classes or being truant not only goes against societal rules but is also considered "deviant", leading to social and legal repercussions.</p>
 
-<p> The transformation in how Jeremy was perceived and treated is a classic example of labeling theory in action.
-"Once labeled, you're playing a part scripted for you by those labels," Jeremy says.
-This script was reinforced continually by the detentions and the reactions of his teachers and peers.
-"When you hear 'Wah, bro finally showed up?' enough times, you start to wonder if trying is worth it," he admits.
+![](docs/src/images/stat.png){fig-align="center" width="545"}
 
-### Breaking Free
+<p>
 
-<p> The turning point came with the passing of his father.
-This profound loss forced Jeremy to reassess his life's direction.
-"It made me realize the shortness of life and the long-term consequences of my choices," he states.
-Motivated by his father's memory and the need to support his family, Jeremy began to shed his truant identity.
-"I was more than my circumstances," he asserts.</p>
+</p>
 
-### Insights from Educators
+<p>Employing a life history interview approach, this essay explores how labelling influences "Jeremy" -- a pseudonym -- finds himself consistently confronted with the repercussions of being labelled as a "truant".
+Therefore, using truancy and the Education Act as a backdrop, the article will discuss the impacts of societal responses on shaping Jeremy's identity and also explore his initial behaviours, the impact of the punishments and the motivations that influenced his persistence in truancy during his time in a local secondary school.</p>
 
-<p> Educators like Mrs.
-Tan, Jeremy's guidance counselor, emphasize the importance of understanding each student's context.
-"We need to look beyond the behavior to the person behind it.
-Only then can we truly help," she notes.
-Mrs.
-Tan advocates for a system that prioritizes supportive measures over punitive ones, suggesting, "Reintegration, not isolation, is key to turning lives around." </p>
+### Methodology
+
+<p>An hour-long interview was conducted face-to-face in his university hall residence.
+Having known Jeremy - the interviewee - for five years, his willingness to participate facilitated an open discussion.
+This allowed him to be honest in sharing his responses, thereby creating a more comprehensive interview.
+The interview hopes to address his experiences and societal influences that perpetuate his role as a "truant" within Singapore's educational system.</p>
+
+### Initial Challenges
+
+<p>Jeremy's journey into truancy began subtly, with his behaviours initially deemed to be minor acts.
+During his time in secondary school, Jeremy had decent grades, great co-curriculum activities (CCA) records, and well-liked by everyone.</p>
+
+<p>However, his life took an unexpected turn when his father fell ill.
+His mother had to reduce her working hours to care for his father.
+Being middle class, Jeremy started to pick up part-time jobs to financially support the family.
+The additional burden started to affect his well-being, physically and mentally resulting in him being late for school -- a deviant behaviour according to Asiyai (2019).</p>
+
+### Escalation to Secondary Deviance
+
+<p>His exhaustion began to manifest, and his tardiness became frequent and got the attention of his friends and teachers.
+When inquired about his late coming, his teacher said he "should be responsible for his actions", which stood out.
+He retaliated and had to serve detention hours during and after class.</p>
+
+<p>The detentions given by the discipline master were originally intended for corrective measures.
+According to Salovitta (2017), school detentions are widely used as a method of punishment.
+However, such practices can alienate, seclude and deprive the student of classes and interactions with their friends.
+Soon, detentions became a routine, inadvertently becoming a part of his secondary school life as he started to miss a full day of classes.</p>
+
+### The Label Begins
+
+<p>During the interview, Jeremy mentioned a term used by this school to describe his offence.
+"Truancy & Repeated Latecomer Offender".
+Furthermore, the detentions exposed him to other students who were deviant actors, reinforcing his behaviours and validating his identity within this marginalised group.</p>
+
+<p>While undergoing his punishment, he began to internalise the label "truant", given by his discipline master, which influenced his self-perception and behaviours.
+This would indicate that the measures of detention fail to address the underlying problem, but further perpetuate deviant identities, leading to a "self-fulfilling prophecy" (Merton, 1968)</p>
+
+### Discussion Using Theoretical Frameworks
+
+#### Lemert's and Becker's Labelling Tradition
+
+<p>Applying Lemert's (1951; 1967) Labelling Tradition suggests that societal reaction to minor acts of deviance can drive individuals to exhibit serious behaviours that are consistent with the associated label.
+Skaggs (2024) asserts, citing Becker (1963), that the sequence from "primary" deviance, where the initial unnoticed and minor acts are labelled as deviant by society.
+As a result, the internalisation of the status by the individual would eventually accept this label as part of their identity, compelling them to adopt these behaviours more consistently, thus transitioning into "secondary" deviance.</p>
+
+![](docs/src/images/remark.png){fig-align="center" width="383" height="52"}
+
+<p>Jeremy's initial label of a "latecomer" soon solidified into a more damaging label of "truant".
+Jeremy's inability to conform to the school norms led to a negative reaction from both his peers and teacher.
+His classmates would often remark, "Wah, bro finally show up?" or "Eh not late today?", indicating a deeper societal rejection, pushing him further into the role his classmates gave him, despite making efforts to avoid tardiness.</p>
+
+<p>As Jeremy's labels transition, it reinforces his deviant identity, making it even more difficult for him to break the cycle and return to a conformist path -- an observation of Durkheim on the functions of deviance in society (Thorlindsson, & Bernburg, 2004).
+Society used its power to label Jeremy, which acted as a barriers, cutting him off from resources that could help him to reintegrate him back to the legitimate school environment, the classroom, instead of the illegitimate -- the detention room.</p>
+
+#### Merton's Strain Theory
+
+<p>Merton's Strain Theory (1957; 1968) provides a framework to further understand Jeremy's "truancy" as a coping mechanism and adaptation to the socially accepted goal.
+According to a study done by Curci and Greco (2016), those who exhibit negative emotions such as stress or anger, are more likely to participate in deviant behaviours.</p>
+
+<p>The emotional distress from his situation triggered his adaptation responses.
+It is important to also note that before committing the deviant act, Jeremy acknowledges that he needs to succeed academically to ensure he meets the societal expectations for material success.
+However, his father's unexpected illness created an economic strain that conflicted with his academic goals at that time.
+According to Merton's theory, his workaround and "truancy" can be classified as an innovative adaptation where his unconventional means to earn extra money conflicted with institutional norms</p>
+
+#### Cohen's Subculture Theory
+
+<p>Cohen's Subculture Theory (1955) plays a part in Jeremy's transition from primary to secondary deviance.
+Cohen (1955) states that subculture -- which refers to a group rejected by society, having shared norms and values -- arises in response to similar strains experienced by individuals.</p>
+
+<p>Phrases like, "come to school late also get detention, might as well don't come" , "no point also la, the teachers don't care about us" and "never mind, join us can already" reflects a shared norm within this subculture of frequent detainees that normalises deviant behaviour.
+While detention is used to maintain social order in school, these exclusionary practices can eventually lead to undesirable labels, and alienation, and could encourage them to engage in secondary deviant roles (Gerlinger et al., 2021).</p>
+
+#### Sutherland's Social Learning Theory
+
+<p>At this point, Jeremy began to skip a full day of classes to work instead.
+Eventually, detention sessions became a classroom for learning truancy.
+For instance, his constant interaction with other repeat offenders provided a social context where he could observe, learn and also internalise the behaviours.</p>
+
+<p>These conversations of deviant behaviours became normalised, which provided Jeremy with specific techniques for skipping full days of classes such as falsifying medical certificates and forging letters of absence from parents.</p>
+
+<p>These experiences are reminiscent of Sutherland's Social Learning Theory where he posits that deviant acts are learned and intensified due to the exposure from his deviant peers (Matsueda, 2010).
+According to Wein (2022), teenagers are very responsive to peer influence and are activated by things they view as beneficial.</p>
+
+<p>He started smoking to "relieve stress", which leading him to smuggle packs of cigarettes for his new-found deviant friends.
+Jeremy's deviant behaviours became a learned lifestyle, only picking it up after serving detention hours.</p>
+
+### Desistance from Deviance
+
+<p> Jeremy’s desistance from deviance can be explored through Hirschi’s (1969) Social Bond Theory.
+Kotlaja and Meier (2018), cited Hirschi (1969), mentioned that bonds such as family or community can deter deviant behaviours.
+In the interview, Jeremy mentioned that his father’s health deteriorated quickly and unfortunately passed away four months later.</p>
+
+<p> These social breaks occurred once he realigned his behaviours to ensure that he could provide support for his family through proper education, and as a result, started attending school regularly and is now pursuing an undergraduate degree in a local university in Singapore.
+His personal loss and familial responsibility align closely with Hirschi’s theory which emphasises the importance of social ties and deterring deviance.
+</p>
 
@@
 
-<p> Jeremy's narrative is a reminder of the complexity of deviance within Singapore's educational system.
-His experiences underscore the critical need for educational policies that foster understanding and provide genuine support.
-As Jeremy continues his journey, now a student at a university in Singapore, his story offers hope and a call to action for all involved in shaping young lives.
-"Change starts when we choose to see the person, not just the problem," Jeremy concludes.</p>
+Well, the 10-year Compulsory Education Act has set an expectation for educational attainment, and would be considered deviant if one fails to comply.
+However, Jeremy’s journey through primary and secondary deviance illuminates the complexities of societal labelling and pressures.
+His experiences highlight the need to support reintegration over unproportionate measures, to foster a healthier school environment for all students.
 
 </details>
-
-<details>
-<summary> Article 3 <br> <p style="text-align: justify;"></p></summary>
-
-## Under Construction
-
-<p style="text-align: right;"> Monday, 6 Nov 2023 </p>
-
-![](docs/src/images/soon.avif){width="730"}
-
-</details>

### 2024-06-19 articles.qmd
Update

@@
 
-<summary> Singapore's Public Housing Affordability <br> <br>  <p style="text-align: justify;"> In Singapore, housing affordability has been an increasing worry for future Singaporeans.
+<summary> Singapore's Public Housing Affordability <br> <br>  <p> In Singapore, housing affordability has been an increasing worry for future Singaporeans.
 However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
@@
 
-<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p style="text-align: justify;"> This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
+<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p> This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
 Read more here...

### 2024-10-11 index.qmd
update
update

--- 2024-05-09 index.qmd
@@
 
-## My Hello to You \~
+## My Hello to You \~\~
 
@@
 <blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">
-
     <section>
-
         <a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>
-
         <p>overland travel for the vibesss</p>
-
         <a target="_blank" title="♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗" href="https://www.tiktok.com/music/original-sound-7178872451673459457?refer=embed">♬ original sound - 𝚁𝚊𝚐𝚑𝚊𝚍💗</a>
-
     </section>
-
 </blockquote>
 
-```{=html}
-<script async src="https://www.tiktok.com/embed.js"></script>
-```
-> </blockquote>
-
-<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7238779076528442625" data-video-id="7238779076528442625" style="max-width: 605px;min-width: 325px;">
-
+<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">
     <section>
-
         <a target="_blank" title="@mentaikofries_" href="https://www.tiktok.com/@mentaikofries_?refer=embed">@mentaikofries_</a>
-
-<p>nha trang is my favvvvvv</p>
-
-<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>
-
+        <p>errr i drank about 9 cups of pearl milk tea in 4 days 3 nights 🇹🇼🥴🧋🇹🇼</p>
+        <a target="_blank" title="♬ fish in the pool・花屋敷 - ヘクとパスカル" href="https://www.tiktok.com/music/fish-in-the-pool-花屋敷-6910585281334740994?refer=embed">♬ fish in the pool・花屋敷 - ヘクとパスカル</a>
     </section>
-
 </blockquote>
 
-```{=html}
 <script async src="https://www.tiktok.com/embed.js"></script>
-```
 :::
@@
 ## National University of Singapore
+
+### Digital Storytelling
+
+During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind.
+He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.
+
+{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}
 
@@
 
-![](docs/src/images/brochure.png)
+::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
+<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
 
-### Design Thinking
+</iframe>
+:::
 
-In this module, we were assigned the task of innovating everyday chores.
-Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe!
+<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>
 
-![](images/prototyping.png){fig-align="center"}
-
-The actual prototyping journey was not very smooth, but hey, here is the end product! Looks good aye? To me at least...
-
-![](images/prototyping_2-01.png)
-
-## Temasek Polytechnic
+### Temasek Polytechnic
 

### 2025-01-24 about.qmd
Update
2025 Update

@@
 **National University of Singapore**\
-*Bachelor of Social Sciences \[Hons.\], Communications New Media / Sociology, Social Sciences* <br> Aug 2022 - Present
+*Bachelor of Social Sciences \[Hons.\], Interactive Media Development/ Sociology, Social Sciences* <br> Aug 2022 - Present
 
@@
 
-**Product Specialist**\
-*Apple South Asia* <br> Aug 2023 - Present · 4 mos
+**Specialist**\
+*Apple South Asia Pte. Ltd.* <br> Aug 2023 - Present
 
@@
 
-**Marketing Research Intern**\
+**Marketing Intern**\
 *Shopee Jakarta, Indonesia· Internship* <br>Mar 2020 - Apr 2020 · 2 mos
@@
 *Sentosa Development Corporation · Part-time* <br>Oct 2013 - Nov 2015 · 2 yrs 2 mos
+
+## Contact Details
+
+For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com

### 2025-01-24 articles.qmd
2025 Update

@@
 
-<summary> Singapore's Public Housing Affordability <br> <br>  <p> In Singapore, housing affordability has been an increasing worry for future Singaporeans.
-However, in 2012, the then Deputy Prime Minister (DPM) Tharman Shanmugaratnam - stating household income of SGD\$1000 was sufficient to own a home, sparked discussions among netizen online (Tan, 2012).
-Read more here...
-</p> </summary>
+<summary>Singapore's Public Housing Affordability <br> <br> <p>In Singapore, housing affordability has become an increasing concern for future Singaporeans.
+However, in 2012, then-Deputy Prime Minister (DPM) Tharman Shanmugaratnam stated that a household income of SGD \$1,000 was sufficient to own a home, sparking discussions among netizens online (Tan, 2012).
+Read more here...</p></summary>
 
@@
 
-While Mr Tharman argued the housing grants could provide support for low-income household, many Singaporeans expressed concern about the long-term viability of such claims, especially in the face of the constant rising cost of living and property prices.
+While Mr.
+Tharman argued that housing grants could provide support for low-income households, many Singaporeans expressed concerns about the long-term viability of such claims, especially in the face of the constantly rising cost of living and property prices.
 
@@
 
-Now, this brings an important question to whether public housing in Singapore truly affordable for the average Singaporean in the future.
-This analysis will also explore the evolving housing market that may impact the affordability of homes for future generations of Singaporeans.
+This brings up a big question---will public housing in Singapore really stay affordable for the average Singaporean in the future?
+In this post, we\'ll take a closer look at how the housing market is evolving and what it could mean for future generations trying to own a home.
 
@@
 
-The above concerns will uncover the complexities of the housing market, analyse potential long-term trend, also seek to understand that while variables such as estate, size or remaining lease play significant roles, this analysis aims to identity the most influential factors.
+We'll dive into the complexities of the housing market, analyze potential long-term trends, and explore how factors like estate, size, and remaining lease impact affordability.
+Ultimately, this analysis aims to identify the key factors that matter most.
 
@@
 
-According to Kumar (2022), the affordability of homes in Singapore is a multifaceted issue.
-The table above provides an outline of the housing prices in Singapore.
-Using this as a guide, it determines the average salary needed per spouse needed to comfortably afford monthly repayments.
+According to Kumar (2022), housing affordability in Singapore is a complex issue with many moving parts.
+The table above outlines current housing prices, offering a useful guide to understanding the financial commitment involved.
+Based on this data, it estimates the average salary each spouse would need to comfortably manage monthly repayments.
 
@@
 
-For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230.
-While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
+For example, to afford a 3-room flat with a median price of \$360,000, both partners would need to earn at least SGD \$5,230 each.
+While this may seem manageable at first glance, it doesn\'t take into account other living expenses or potential income fluctuations.
+Couples may have additional financial commitments, such as owning a car or raising multiple children, which can significantly impact their overall affordability.
 
@@
 
-Imagine you and your sponse are looking to start a family.
-Now that we've a glimpse into the affordability of homes in Singapore, do you think you can comfortably own your own home when the time comes?
-Let's dive into real data and discuss this critical issue further.
+magine you and your spouse are planning to start a family.
+Now that we\'ve taken a glimpse into the affordability of homes in Singapore, do you think you\'ll be able to comfortably own your own home when the time comes?
+Let\'s dive into the real data and explore this critical issue further.
 
@@
 
-Before moving on to the deeper analysis, let us understand how the overall prices have increased from 1990 to 2022.
-While the general increase in prices overtime aligns with economic growth, the rate of the surge from 1990 to 2022 is alarming.
+Before diving deeper into the analysis, let's first take a look at how housing prices have increased from 1990 to 2022.
+While the general upward trend in prices aligns with Singapore's economic growth, the rapid surge over this period is quite alarming.
 
@@
 
-One may argue that the increment is a sign of prospering economy, on the other side, it also rings alarm bells in terms of overall affordability. Now let's examine the graph below:
+Some might argue that the rising prices are a reflection of a thriving economy.
+However, on the flip side, they also raise serious concerns about overall affordability.
+Now, let's take a closer look at the graph below to better understand the trends:
 
@@
 
-The graph above illustrates a significant steepening in the slopes of average resale prices in Singapore from 1990 to 2022 - indicating the exorbitant increase of prices across all flat types.
-The steeper slope in 2022 shows a more prominent price escalation as compared to 1990's.
-This is can be an indication increasing pressure on affordability and financial stretch for home ownership.
+The graph above shows a significant steepening in the trend of average resale prices in Singapore from 1990 to 2022, highlighting the sharp rise in housing costs across all flat types.
+The steeper slope in 2022 reflects a more pronounced price escalation compared to the 1990s.
+This trend could indicate growing pressure on affordability and an increasing financial strain for prospective homeowners.
 
@@
 
-Notice that on the graph, there is a worrying widening price gap between each successive flat type, with the difference in average prices from one flat type to the next becoming more distinct.
-For example, the price jump from a 3-room to a 4-room for both 1990 and 2022, may point towards a growing demand for a larger home.
-Larger home, bigger family right?
+Notice on the graph that there\'s a concerning widening price gap between each successive flat type, with the difference in average prices becoming more pronounced over time.
+The jump in prices from a 3-room to a 4-room flat, both in 1990 and 2022, suggests a growing demand for larger homes.
+After all, a bigger home often means plans for a bigger family, right?
 
@@
 
-With that, we can understand that the widening gap of prices could create a cost burden for upgraders seeking more specious accommodations for a bigger family.
-The growing gap in prices shows that planning for home ownership is extremely crucial to prevent any buyers' remorse.
+With that in mind, the widening price gap could pose a significant financial burden for upgraders seeking more spacious accommodations for a growing family.
+This increasing disparity highlights the importance of careful planning when it comes to home ownership to avoid potential buyer's remorse in the future.
 
@@
 
-Now let's look at the price increment individually for both years, compared with the same flat type. The graph presented shows a great difference for a 4-room flat between 1990 and 2022.
+Now, let\'s take a closer look at the price increases for each flat type individually across both years.
+The graph highlights a significant difference in the cost of a 4-room flat between 1990 and 2022.
+This stark contrast underscores how much prices have surged over the years, emphasizing the growing challenge of affordability for aspiring homeowners.
 
@@
 
-The year 1990 with an average price of SGD\$81,525 and 2022 with an average price of SGD\$525,092, represented by green and orange respectively.
-In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022!
+In 1990, the average price of a 4-room flat was SGD \$81,525, while in 2022, it skyrocketed to SGD \$525,092---represented by green and orange markers on the graph, respectively.
+Check out the graph below to explore and compare the prices of other flat types between 1990 and 2022!
 
@@
 
-As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options.
-Additionally, the graph suggests that the real estate market has become increasingly segmented.
-Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020).
+As mentioned earlier, the rising trend in housing costs, as shown in the graph, suggests that potential homeowners may face significant financial barriers when searching for suitable housing options.
+Furthermore, the data indicates that the real estate market has become increasingly segmented over time.
+Unfortunately, with growing demand and limited supply, property agents are capitalizing on the eagerness of potential homebuyers (Lam, 2020).
 
@@
 
-For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019).
-To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market.
+For instance, in 2019, a property agent was found guilty of engaging in unethical bidding practices to secure a higher commission (Lim, 2019).
+To address such issues, regulatory bodies must implement and enforce strict rules and guidelines to promote fair practices in this highly competitive and high-stakes market.
 
@@
 
-While a price increment can potentially indicate a critical issue with affordability, it is also important to access where the increase is still within the "safe" median range.
-However, in the box plot below, we can see how the presence of outliers underscores the significant and unprecedented price increase.
+While rising prices can signal affordability concerns, it\'s important to assess if they remain within a "safe" median range.
+However, the box plot below shows outliers that highlight significant and unprecedented price surges, raising concerns about long-term affordability.
 
@@
 
-Furthermore, across the other flat types, there is an increasing number of outliers beyond the upper whiskers of the box plots for 2022.
-While this can suggest a substantial market growth, it can also reflect the high number of exceptional cases where resale prices are charging a even higher premium, exceeding the median trends - which is already high.
+Furthermore, across other flat types, the increasing number of outliers beyond the upper whiskers of the 2022 box plots suggests substantial market growth.
+However, it also indicates a rising number of exceptional cases where resale prices are commanding even higher premiums---far exceeding already high median trends.
 
@@
 
-Now, that we have clearly seen the high prices Singaporean are willing to pay for their dream home, are there other factors that can be attributed to the price increase?
-Next, we will explore if the remaining lease left or the location of the flat affect the resale price.
+Now that we've seen the high prices Singaporeans are willing to pay for their dream home, what other factors could be driving these increases?
+Next, we'll explore whether factors such as the remaining lease or the flat's location play a significant role in resale prices.
 
@@
 
-To lower the cost burden for flat upgraders, some may consider purchasing a flat with a lower remaining lease.
-However, is there a correlation between the remaining lease and the cost of a resale flat in 1990 and 2022?
+To ease the financial burden, some flat upgraders may consider purchasing a flat with a shorter remaining lease.
+But does the remaining lease actually correlate with the resale flat prices in 1990 and 2022?
+Let's take a closer look at whether this factor influences affordability over time.
 
@@
 
-As we look and examine into the numbers, it becomes clear that patterns have shifted from 1990 to 2022.
-Here, we will be comparing the data from these two distinct years.
-Now let's look at the scatterplot below.
-Pay attention to the red line, what does it tell you?
+As we dive into the numbers, it\'s clear that patterns have shifted significantly from 1990 to 2022.
+In this section, we\'ll compare data from these two distinct years to uncover key trends.
+Now, take a look at the scatterplot below---pay close attention to the red line.
+What does it reveal about the relationship between remaining lease and resale prices?
 
@@
 
-In 1990, the line suggested a clear trend: where a longer remaining lease often correlated with a higher resale price.
-The regression line showed a noticeable upward slope; decently steep actually.
-This would indicate that the longer the remaining lease, the higher the resale price of the flat, which makes sense at the time where buyers could reside in the flat without facing any lease expiration issue in the future.
+In 1990, the trend was clear---a longer remaining lease often meant a higher resale price.
+The upward slope of the regression line was quite steep, indicating that buyers valued flats with longer leases, as they provided long-term security without lease expiration concerns.
 
@@
 
-However, as we move to 2022, while there is still a correlation, we can observe that it is not as steep.
-This suggests that the remaining lease period is not as strong an indicator as it was in 1990.
-Also, the data points are more spread out , indicating a high variance in resale prices.
-We can now infer that other factors such as location, types or houses, or amenities have grown in importance of lease length when determining the value of the resale flat.
+In 2022, while there's still a correlation, the slope is less steep, suggesting that the remaining lease is no longer as strong an indicator as it was in 1990.
+The data points are more spread out, showing greater variance in resale prices.
+This indicates that factors like location, flat type, and amenities have become more important than lease length in determining a flat's value.
 
@@
 
-Put yourself in the shoes of the buyer, would you get a house with longer remaining lease, but with everything else an hour away or a shorter remaining lease with everything else a stone's throw away?
+Put yourself in the buyer's shoes---would you prefer a flat with a longer remaining lease but located an hour away from everything, or a shorter lease with all the conveniences just a stone's throw away?
 
@@
 
-The answer is not merely a matter of counting the years on a lease.
-So far, none of the HDB flats have seen their lease expired.
-So no one knows what really happens after that.
-Buying your own home is also about weighing the value or time and quality of your daily life.
-After all, what is a good extended lease if it comes at an expense of your convenience and time?
-Now, we will look into another important factor: The Estate
+The answer isn't just about counting the years left on a lease.
+So far, no HDB flat has reached the end of its lease, leaving uncertainty about what truly happens next.
+Buying a home is also about balancing the value of time and quality of life.
+After all, what's the point of a long lease if it comes at the expense of convenience and daily comfort?
+Now, let's dive into another crucial factor: the estate.
 
@@
 
-We can agree that price is an important consideration for purchasing a home.
-Have you figured out where to live?
-Do you want to live close to your parents in the same estate?
-Or do you have a preferred school you would like to send your future children too?
-Now, we will examine if the estate affects the price of the resale flat.
-We will also determine which estate tends to be more costly or cheaper to settle down.
+Price is undoubtedly a major factor when purchasing a home, but have you decided where to live?
+Would you prefer to stay close to your parents in the same estate, or do you have a specific school in mind for your future children?
+Next, we'll explore how the estate impacts resale flat prices and identify which areas tend to be more expensive or budget-friendly for settling down.
 
@@
 
-Now, let's explore the violin plot on the interactive dashboard.
-For visualisation, we will use Bukit Timah and Punggol.
-According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is known for it access to many well sought after educational institutes such as Hwa Chong Institutions, National Junior College and Raffles Girls' Primary School, making it one of the most popular estate.
+Now, let's explore the violin plot on the interactive dashboard, focusing on Bukit Timah and Punggol.
+According to 99.co (n.d), [Bukit Timah](https://www.99.co/singapore/neighbourhoods/bukit-timah) is popular for its proximity to top schools like Hwa Chong Institution, National Junior College, and Raffles Girls' Primary School, making it a highly sought-after estate
 
@@
 
-[Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate.
-It is slowly becoming popular with younger couples due to its modern amenities and promising development plans.
-The town is being developed with a vision to be eco-friendly, sustainable while providing trendy lifestyle hubs that cater to all age groups.
+[Punggol](https://www.99.co/singapore/neighbourhoods/punggol), on the other hand, is a relatively new estate that\'s gaining popularity among younger couples.
+With modern amenities and promising development plans, it\'s being designed as an eco-friendly and sustainable town, offering trendy lifestyle hubs that cater to all age groups.</p>
+
+<p style="text-align: justify;">
+
+With that in mind, let's analyze the violin plot.
+We can observe a wider distribution of resale prices, with a more pronounced upper tail.
+This suggests a greater variety of flats available, while also highlighting a substantial market for high-end luxury units.
 
@@
 
-That being said, let's analyse the violin plot.
-We can observe the wider distribution of resale prices, with a more pronounced upper tail.
-This would indicate there are a larger variety of flats, but also a substantial market for high-end luxury flats.
-
-</p>
-
-<p style="text-align: justify;">
-
-On the flip side, Punggol has a narrower but dense concentration of price, indicating a more concrete (or less variation) in resale prices.
-Now, let's interact with the plot, select your dream estates and explore the price variations!
-Oh and just in case, I'll put the MRT Map here for reference!
+On the flip side, Punggol shows a narrower but denser concentration of prices, indicating less variation in resale prices.
+Now, go ahead and interact with the plot---select your dream estates and explore the price differences!
+And just in case, I've included the MRT map here for easy reference!
 
@@
 
-Now, if we were to deduce on which is the best place to settle down based on what we have gathered, the decision really depends on what you value the most.
-For instance, if you value tranquility and a sea view, Punggol would be great.
+Ultimately, deciding the best place to settle down depends on what matters most to you. If you prioritize tranquility and scenic sea views, Punggol might be the perfect fit.
 
@@
 
-However, if you would like be in close proximity of prestigious schools, *(all schools are good schools - but let's not get into that for now)* then Bukit Timah might be the best choice for you!
-The visualisation does not only tell us about the prices, but also a reflection of lifestyle, and the long-term family vision for you and your spouse!
+However, if being close to prestigious schools is your priority (yes, all schools are good schools---but let's not get into that), then Bukit Timah might be the better choice.
+These visualizations not only reveal price trends but also reflect lifestyle preferences and your long-term family vision.
 
@@
 
-Year-on-year, the prices of resale HDB flats have seen a continuous rise, reflecting in a growing demand of housing solutions in Singapore.
-However, this brings concerns to many Singaporeans, especially younger couples intending to start a family, as they struggle with affordability and availability issues.
+Year after year, resale HDB prices have continued to rise, reflecting the growing demand for housing in Singapore.
+However, this trend raises concerns for many Singaporeans, especially younger couples looking to start a family, as they face increasing challenges with affordability and availability.
 
@@
 
-According to recent reports, analysts indicated that prices of resale flats are expected to rise moderately for the remainder of 2023 (CNA, 2023).
-While cooling measures have taken place to control the prices, the growth in the third quarter of 2023 was due to price resistance setting in amid inflationary and affordability concerns.
+Recent reports indicate that analysts expect resale flat prices to rise moderately for the rest of 2023 (CNA, 2023).
+While cooling measures have been implemented to control prices, the growth observed in the third quarter of 2023 was driven by price resistance amid inflation and affordability concerns.
 
@@
 
-You might be thinking - " Aren't there build-to-order (BTO) flats that are way priced way lower with other grants for purchase?" - and you know what, you are absolutely right!
-But are you willing to ballot with tens and thousands of couples, wait 5-6 years, and then face the possibility of being turned down?
-Certainly, the choice to ballot for a BTO flat, despite its lower cost and readily available grants, requires risk-taking and uncertainties.
+You might be thinking, \*"Aren't there Build-to-Order (BTO) flats that are much cheaper with grants available?"\* And you're absolutely right!
+But are you ready to compete with tens of thousands of couples, wait 5-6 years, and still risk not getting a flat?
+Choosing to ballot for a BTO, despite its lower cost and grants, comes with its fair share of uncertainties and risks.
 
@@
 
-Therefore, this analysis could provide a thoughtful evaluation of the need for immediate housing against the potential delays and challenges of the BTO process.
-For now, all we can do is leverage on the available grants and ensure that we spend on what we can afford.
+This analysis offers a thoughtful evaluation of the need for immediate housing versus the potential delays and challenges of the BTO process.
+For now, the best approach is to make the most of available grants and focus on purchasing within our means.
 
@@
 
-<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p> This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
-Read more here...
-</p> </summary>
+<summary> Educational Deviance in Singapore: A Case Study of Truancy and Societal Reaction <br> <br> <p>This study examines the impact of labeling on student identity within Singapore's educational system through the case of "Jeremy," a student labeled as a "truant." Utilizing a life history interview, the research illustrates how societal reactions and the Compulsory Education Act of 2000 influence behaviors from primary to secondary deviance.
+Read more here...</p></summary>
 
@@
 
-<p style="text-align: right;"> Friday, 10 May 2024</p>
+<p style="text-align: right;">
+
+Friday, 10 May 2024
+
+</p>
 
@@
 
-<p> Jeremy’s desistance from deviance can be explored through Hirschi’s (1969) Social Bond Theory.
+<p>Jeremy's desistance from deviance can be explored through Hirschi's (1969) Social Bond Theory.
 Kotlaja and Meier (2018), cited Hirschi (1969), mentioned that bonds such as family or community can deter deviant behaviours.
-In the interview, Jeremy mentioned that his father’s health deteriorated quickly and unfortunately passed away four months later.</p>
+In the interview, Jeremy mentioned that his father's health deteriorated quickly and unfortunately passed away four months later.</p>
 
-<p> These social breaks occurred once he realigned his behaviours to ensure that he could provide support for his family through proper education, and as a result, started attending school regularly and is now pursuing an undergraduate degree in a local university in Singapore.
-His personal loss and familial responsibility align closely with Hirschi’s theory which emphasises the importance of social ties and deterring deviance.
-</p>
+<p>These social breaks occurred once he realigned his behaviours to ensure that he could provide support for his family through proper education, and as a result, started attending school regularly and is now pursuing an undergraduate degree in a local university in Singapore.
+His personal loss and familial responsibility align closely with Hirschi's theory which emphasises the importance of social ties and deterring deviance.</p>
 
@@
 Well, the 10-year Compulsory Education Act has set an expectation for educational attainment, and would be considered deviant if one fails to comply.
-However, Jeremy’s journey through primary and secondary deviance illuminates the complexities of societal labelling and pressures.
+However, Jeremy's journey through primary and secondary deviance illuminates the complexities of societal labelling and pressures.
 His experiences highlight the need to support reintegration over unproportionate measures, to foster a healthier school environment for all students.

### 2025-01-24 index.qmd
2025 Update

--- 2024-05-09 index.qmd
@@
 
-```{=html}
-<script async src="https://www.tiktok.com/embed.js"></script>
-```
-> </blockquote>
-
-<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7238779076528442625" data-video-id="7238779076528442625" style="max-width: 605px;min-width: 325px;">
+<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">
 
@@
 
-<p>nha trang is my favvvvvv</p>
+<p>errr i drank about 9 cups of pearl milk tea in 4 days 3 nights 🇹🇼🥴🧋🇹🇼</p>
 
-<a target="_blank" title="♬ moth to a flame x after hours - trlixqy" href="https://www.tiktok.com/music/moth-to-a-flame-x-after-hours-7174186663990561579?refer=embed">♬ moth to a flame x after hours - trlixqy</a>
+<a target="_blank" title="♬ fish in the pool・花屋敷 - ヘクとパスカル" href="https://www.tiktok.com/music/fish-in-the-pool-花屋敷-6910585281334740994?refer=embed">♬ fish in the pool・花屋敷 - ヘクとパスカル</a>
 
@@
 
-# **My Past Work**
+## Contact Details
 
-## National University of Singapore
-
-### Social Thought and Theory
-
-In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
-This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
-
-Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
-How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
-
-{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
-
-### Artificial Intelligence and Society
-
-In this module, we looked at the benefits and potential downsides of relying on AI.
-My group focused on leveraging on AI technology to aid in bereavement process.
-I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with their loved ones - as an avatar!
-
-![](docs/src/images/brochure.png)
-
-### Design Thinking
-
-In this module, we were assigned the task of innovating everyday chores.
-Here is my idea: it is basically an attachment that can be clipped to an existing ironing board, so that people - including the elderly or people with disabilities - can iron clothes without feeling tired or unsafe!
-
-![](images/prototyping.png){fig-align="center"}
-
-The actual prototyping journey was not very smooth, but hey, here is the end product! Looks good aye? To me at least...
-
-![](images/prototyping_2-01.png)
-
-## Temasek Polytechnic
-
-### Savvify - An Automated Savings Platform
-
-During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***.
-Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.
-
-Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!
-
-{{< video https://youtu.be/kzWq31_mRyc >}}
-
-### GIGAWipes - Innovation through Programming
-
-"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives.
-This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but...
-I'll let the video do the talking...
-
-{{< video https://youtu.be/2yBwaRCfiuI >}}
-
-Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms
-
-```         
-```
+For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com or visit my [LinkedIn Page](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
 

### 2025-01-24 interests.qmd
update
update
2025 Update

@@
 ---
-title: "My Interests"
+title: "My Past Work"
 ---
 
-![](docs/src/images/soon.avif){width="730"}
+```{r, eval=TRUE,echo=FALSE}
+```
+
+## National University of Singapore
+
+### Digital Storytelling
+
+During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind.
+He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.
+
+{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}
+
+### Social Thought and Theory
+
+In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
+This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
+
+Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
+How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
+
+{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
+
+### Artificial Intelligence and Society
+
+In this module, we looked at the benefits and potential downsides of relying on AI.
+My group focused on leveraging on AI technology to aid in bereavement process.
+I designed a brochure for a Virtual Memory Garden where users will transported into a virtual space together with their loved ones - as an avatar!
+
+::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
+<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
+
+</iframe>
+:::
+
+<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>
+
+### Temasek Polytechnic
+
+### Savvify - An Automated Savings Platform
+
+During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***.
+Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.
+
+Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!
+
+{{< video https://youtu.be/kzWq31_mRyc >}}
+
+### GIGAWipes - Innovation through Programming
+
+"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives.
+This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but...
+I'll let the video do the talking...
+
+{{< video https://youtu.be/2yBwaRCfiuI >}}
+
+Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms
+
+```         
+```
+
+![](src/images/footer.png)

### 2025-01-28 index.qmd
Update

@@
 
-Hello there! My name is Marzuki Nooranas - or *Marz* for short! I am currently in my 3rd year, double majoring in Sociology and Communications & New Media!
+Hello there!
+My name is Marzuki Nooranas \[[Resume](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)\] - or *Marz* for short!
+I am currently in my 3rd year, majoring in Sociology and Interactive Media Development!
 
@@
 
-For any opportunities, you can reach me via my email - marzukinooranas\@gmail.com or visit my [LinkedIn Page](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
+For any opportunities:
 
-![](src/images/footer.png)
+Email - marzukinooranas\@gmail.com
+
+Linkedin - [Marzuki Nooranas](https://www.linkedin.com/in/marzuki-nooranas-b5947b17a/)
+
+Resume - [Download](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)
+
+```         
+```

### 2025-01-28 interests.qmd
Update

@@
 
-## National University of Singapore
+<br> I've dabbled in UX/UI design and video editing, mostly picking up these skills on my own because I'm really into it.
+I love creating cool user experiences and videos that pop, and I'm excited to keep leveling up and bringing more creativity to my work!
 
-### Digital Storytelling
+# UX/UI Prototyping and Design Work
 
-During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind.
-He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.
+## Interaction Design
 
-{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}
+### (1) SlideCraft - AI Powered Design Tool
 
-### Social Thought and Theory
+SlideCraft is an AI-powered slide design tool created to simplify the presentation-making process for students and educators.
+I developed detailed lo-fi and hi-fi prototypes, focusing on features like design consistency, personalized recommendations, and efficiency.
 
-In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
-This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
+This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions​
 
-Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
-How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>
 
-{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
+</iframe>
 
-### Artificial Intelligence and Society
+### (2) GPTDashboard - Desktop and Mobile View
+
+The ChatGPT Dashboard was designed to help social media content creators streamline their workflow by integrating AI into content generation and tracking.
+I worked on both lo-fi and hi-fi prototypes, ensuring a smooth user experience across desktop and mobile views.
+
+This project focused on addressing key pain points like burnout and content optimization while providing real-time feedback metrics to help creators stay on top of trends​
+
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>
+
+</iframe>
+
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-155&amp;starting-point-node-id=1%3A155&amp;embed-host=share" allowfullscreen>
+
+</iframe>
+
+### (3) SaveWatt
+
+SaveWatt is a digital platform aimed at helping homeowners make smarter, energy-efficient appliance choices amidst rising electricity tariffs.
+I contributed to the design of a user-friendly interface that consolidates appliance comparison tools, offering personalized recommendations and energy-saving insights.
+
+This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way​
+
+Full PortFolio: <https://savewatt.framer.website>
+
+![](src/images/SaveWatt.png)
+
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>
+
+</iframe>
+
+## TeachSG
+
+For my TeachSG attachment, I created this motivational card specifically for primary school students who were struggling with math.
+The card was designed to inspire confidence and encourage them as they prepared for their PSLE exams.
+
+Using bright colors, cheerful designs, and a personalized touch with mentor memojis, I aimed to make the card relatable and uplifting, helping the students feel supported and motivated to achieve their best.
+
+::: {style="position: relative; width: 100%; height: 0; padding-top: 56.2225%; padding-bottom: 0; box-shadow: 0 2px 8px 0 rgba(63,69,81,0.16); margin-top: 1.6em; margin-bottom: 0.9em; overflow: hidden; border-radius: 8px; will-change: transform;"}
+<iframe loading="lazy" style="position: absolute; width: 100%; height: 100%; top: 0; left: 0; border: none; padding: 0;margin: 0;" src="https://www.canva.com/design/DAGRwrKGhxo/DFyJSp72gAFRLvh1wU3bwA/view?embed" allowfullscreen="allowfullscreen" allow="fullscreen">
+
+</iframe>
+:::
+
+<a href="https://www.canva.com/design/DAGRwrKGhxo/DFyJSp72gAFRLvh1wU3bwA/view?utm_content=DAGRwrKGhxo&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"></a>
+
+## Artificial Intelligence and Society
 
@@
 
-<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>
+# Video Editing and Production Work
 
-### Temasek Polytechnic
-
-### Savvify - An Automated Savings Platform
+## Savvify - An Automated Savings Platform
 
@@
 
-### GIGAWipes - Innovation through Programming
+## Digital Storytelling
+
+#### Pattoo Tarlour: The Art of the Needle
+
+Here, we interviewed Pattoo Tarlour, a local tattoo business. We explored the artistry, passion, and personal stories behind tattooing in Singapore.
+
+Through interviews with talented artists, visuals of their creative process, and dynamic shots capturing the parlour's ambiance, the documentary highlights the unique culture and meaningful connections that define the space.
+It celebrates the cultural and artistic significance of tattooing as both a craft and an expression of identity.
+
+{{< video https://www.youtube.com/embed/AoD6FvMuHxk?si=t2d06a4Opw8NPRXV >}}
+
+#### Day in the Life: Captured Through Film
+
+During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind.
+He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.
+
+{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}
+
+## Social Thought and Theory
+
+In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
+This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
+
+Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
+How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
+
+{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
+
+<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>
+
+## GIGAWipes - Innovation through Programming
 
@@
 
-![](src/images/footer.png)
+```         
+```

### 2025-01-28 interests.qmd
Update

@@
 
-This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions​
+This project emphasized enabling users to focus on content creation while saving time with AI-driven slide suggestions.
 
@@
 
-### (2) GPTDashboard - Desktop and Mobile View
+### (2) GPTDashboard - Desktop View
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-155&amp;starting-point-node-id=1%3A155&amp;embed-host=share" allowfullscreen>
-
-</iframe>
-
 ### (3) SaveWatt
@@
 
-This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way​
+This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.
 

### 2025-01-28 interests.qmd
Site Update

@@
 :::
-
-# Video Editing and Production Work
-
-## Savvify - An Automated Savings Platform
-
-During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***.
-Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.
-
-Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!
-
-{{< video https://youtu.be/kzWq31_mRyc >}}
-
-## Digital Storytelling
-
-#### Pattoo Tarlour: The Art of the Needle
-
-Here, we interviewed Pattoo Tarlour, a local tattoo business. We explored the artistry, passion, and personal stories behind tattooing in Singapore.
-
-Through interviews with talented artists, visuals of their creative process, and dynamic shots capturing the parlour's ambiance, the documentary highlights the unique culture and meaningful connections that define the space.
-It celebrates the cultural and artistic significance of tattooing as both a craft and an expression of identity.
-
-{{< video https://www.youtube.com/embed/AoD6FvMuHxk?si=t2d06a4Opw8NPRXV >}}
-
-#### Day in the Life: Captured Through Film
-
-During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind.
-He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.
-
-{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}
-
-## Social Thought and Theory
-
-In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim.
-This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.
-
-Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today.
-How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!
-
-{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}
-
-<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>
-
-## GIGAWipes - Innovation through Programming
-
-"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives.
-This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but...
-I'll let the video do the talking...
-
-{{< video https://youtu.be/2yBwaRCfiuI >}}
-
-Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms
-
 ```         

### 2025-01-28 videos.qmd
Site Update

---
title: "My Past Work"
---

```{r, eval=TRUE,echo=FALSE}
```

<br> I've dabbled in UX/UI design and video editing, mostly picking up these skills on my own because I'm really into it. I love creating cool user experiences and videos that pop, and I'm excited to keep leveling up and bringing more creativity to my work!

# Video Editing and Production Work

## Savvify - An Automated Savings Platform

During my time in Temasek Polytechnic, my group mates and I worked on an automated savings platform - ***Savvify***. Essentially, the application helps users to round up your payment transactions to the nearest dollar, and crediting it to the users' e-wallet upon making QR Payments.

Our main goal was to bring new solutions e-payment solutions while helping young adults like us, to understand real life responsibilities - improving their financial literacy!

{{< video https://youtu.be/kzWq31_mRyc >}}

## Digital Storytelling

#### Pattoo Tarlour: The Art of the Needle

Here, we interviewed Pattoo Tarlour, a local tattoo business. We explored the artistry, passion, and personal stories behind tattooing in Singapore.

Through interviews with talented artists, visuals of their creative process, and dynamic shots capturing the parlour's ambiance, the documentary highlights the unique culture and meaningful connections that define the space. It celebrates the cultural and artistic significance of tattooing as both a craft and an expression of identity.

{{< video https://www.youtube.com/embed/AoD6FvMuHxk?si=t2d06a4Opw8NPRXV >}}

#### Day in the Life: Captured Through Film

During a casual cycling session, Marzuki (me) finds himself in an unusual situation -- discovering a photo album and film camera left behind. He takes the opportunity to slow down and capture moments from the day in the lives of everyday people while enjoying his ride.

{{< video https://www.youtube.com/embed/Nz8UhdKpz-Y?si=FymUgJAb4lcMtJB9 >}}

## Social Thought and Theory

In this module, we explored the contributions of the founding fathers of Sociology - Marx, Weber and Durkheim. This Social Media assignment looks into Weber's ideas found in the The Protestant Work Ethic and the Spirit of Capitalism and Bureaucracy.

Here, we discussed (in a very Gen-Z way) that we have to be (economically) productive every single minute of our day, how we should be "growing money even in our sleep" is increasingly prevalent today. How everything we do now is to be justified in economic terms and we end up losing meaning, becoming disenchanted in life - Here's what we did!

{{< video https://www.youtube.com/embed/-SYPjaJoi-I?si=ViXbIgq6TR4Lmbh4 >}}

<a href="https://www.canva.com/design/DAF0lbgxhPk/jKGt5Uqtio2trLaLP-h9tw/view?utm_content=DAF0lbgxhPk&utm_campaign=designshare&utm_medium=embeds&utm_source=link" target="_blank" rel="noopener"> </a>

## GIGAWipes - Innovation through Programming

"Innovation does not stop" -- Here, we explored how to incorporate programming in our daily lives. This may or may not be inspired by true events but for this project, we created a prototype of a toilet roll dispenser but... I'll let the video do the talking...

{{< video https://youtu.be/2yBwaRCfiuI >}}

Not bad aye! Essentially, The lanyard communicates via Bluetooth. this ensures that toilet rolls are filled and readily available for use, maintaining hygiene and convenience in restrooms

```         
```

```         
```

### 2025-01-28 interests.qmd
Update

@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
+src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
+allowfullscreen>
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>
+<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
+src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
+allowfullscreen>
 
@@
 :::
+
 ```         

### 2025-01-28 interests.qmd
Update Responsive

@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">
-
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
-allowfullscreen>
-
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
-allowfullscreen>
-
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
 

### 2025-01-28 interests.qmd
Dropdown

--- 2025-01-28 interests.qmd
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">
-
+<details>
+  <summary style="cursor: pointer; font-weight: bold; padding: 10px; background-color: #f0f0f0; border: 1px solid #ccc;">
+    View SlideCraft Prototype
+  </summary>
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
+</details>
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
-allowfullscreen>
-
+<details>
+  <summary style="cursor: pointer; font-weight: bold; padding: 10px; background-color: #f0f0f0; border: 1px solid #ccc;">
+    View GPTDashboard Prototype
+  </summary>
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&amp;node-id=1-228&amp;starting-point-node-id=1%3A228&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
+</details>
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
-allowfullscreen>
-
+<details>
+  <summary style="cursor: pointer; font-weight: bold; padding: 10px; background-color: #f0f0f0; border: 1px solid #ccc;">
+    View SaveWatt Prototype
+  </summary>
+<div style="position: relative; width: 100%; height: 450px;">
+  <iframe style="position: absolute; top: 0; left: 0; width: 100%; height: 100%; border: 1px solid rgba(0, 0, 0, 0.1);" src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&amp;node-id=89-2546&amp;starting-point-node-id=89%3A2546&amp;embed-host=share" allowfullscreen>
   </iframe>
+</div>
+</details>
 

### 2025-01-28 index.qmd
Update for Mobile

@@
     flex-wrap: wrap;
-  justify-content: center;
-  width: 105%; 
+    justify-content: space-between; /* Distribute space between items */
+    gap: 20px; /* Add spacing between items */
+    width: 100%;
+    max-width: 1200px; /* Limit maximum width for larger screens */
+    margin: 0 auto; /* Center the container */
   }
@@
     box-sizing: border-box;
-  max-width: 100%;
-  flex: 1 1 300px;
-  margin: 0 auto; 
+    flex: 1 1 calc(50% - 10px); /* Two items per row with spacing */
+    max-width: calc(50% - 10px); /* Two items per row with spacing */
+    min-width: 300px; /* Minimum width for each embed */
   }
@@
     .tiktok-embed {
-    min-width: auto;
+      flex: 1 1 100%; /* Full width on mobile */
+      max-width: 100%; /* Full width on mobile */
     }
@@
 ::: tiktok-container
-<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">
+<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161">
 
@@
 
-<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">
+<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168">
 
@@
 </blockquote>
+:::
 
@@
 ```
-:::
-
 ## Contact Details

### 2025-01-28 interests.qmd
Update for Mobile

--- 2025-01-28 interests.qmd
@@
 
-### (1) SlideCraft - AI Powered Design Tool
+### (1) SlideCraft - AI Powered Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">
+[![](src/images/Slidecraft.png)](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
 
-</iframe>
-
-### (2) GPTDashboard - Desktop View
+### (2) GPTDashboard
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
-allowfullscreen>
+#### Desktop View - [Try](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)
 
-</iframe>
+[![](src/images/GPTDashboard.png)](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)
 
-### (3) SaveWatt
+#### Mobile View - [Try](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)
+
+[![](src/images/Mobile Dashboard.png)](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)
+
+### (3) SaveWatt - [Try](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)
 
@@
 
-<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
-src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
-allowfullscreen>
-
-</iframe>
+[![](src/images/SaveWatt_Prototype.png)](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)
 

### 2025-01-28 interests.qmd
Update

@@
 
-### (1) SlideCraft - AI Powered Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
+### (1) SlideCraft - AI Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
 

### 2025-01-28 index.qmd
Picture Update

@@
 
-To demonstrate this, I embark of frequent backpacking trips across Southeast Asia, and actively engage myself in the cultures and learn about their customs.
-
-Such experiences provide me with firsthand insights into how different societies interact, and not only broadening my horizons, but also fostering empathy across different communities.
-Here's a little snippet -
+To demonstrate this, I embark on frequent backpacking trips across Southeast Asia and actively immerse myself in local cultures to learn about their customs.
+These experiences provide me with firsthand insights into how different societies interact, not only broadening my horizons but also fostering empathy across diverse communities.
+Here's a little snippet!
 

### 2025-01-28 interests.qmd
Desktop View
Update

@@
 
-### (1) SlideCraft - AI Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
+### (1) SlideCraft - AI Design Tool - <a href="https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1" target="_blank">Try</a>
 
@@
 
-[![](src/images/Slidecraft.png)](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)
+![](src/images/Slidecraft.png)
 
@@
 
-#### Desktop View - [Try](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)
+#### Desktop View - <a href="https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1" target="_blank">Try</a>
 
-[![](src/images/GPTDashboard.png)](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)
+![](src/images/GPTDashboard.png)
 
-#### Mobile View - [Try](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)
+#### Mobile View - <a href="https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1" target="_blank">Try</a>
 
-[![](src/images/Mobile Dashboard.png)](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)
+![](src/images/Mobile%20Dashboard.png)
 
-### (3) SaveWatt - [Try](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)
+### (3) SaveWatt - <a href="https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1" target="_blank">Try</a>
 
@@
 
-This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.
+![](src/images/SaveWatt_Prototype.png)
 
-Full PortFolio: <https://savewatt.framer.website>
+This project tackled the challenges of decision fatigue and financial strain by providing actionable guidance in a visually engaging way.Full PortFolio: <https://savewatt.framer.website> (Use Desktop View only)
 
 ![](src/images/SaveWatt.png)
-
-[![](src/images/SaveWatt_Prototype.png)](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)
 

### 2025-04-23 videos.qmd
Update

@@
 # Video Editing and Production Work
+
+## Nature Versus Nurture - Podcast Debate in Animation Style
+
+For this project, I focused on experimenting with animation and editing techniques to create a visually engaging, debate-style segment on the topic of transgender athletes in competitive sports.
+I used Canva for design elements, CapCut for assembling motion sequences, and Final Cut Pro for final compositing and audio syncing.
+
+This was a creative testbed where I explored how layered visuals and stylized transitions could enhance both the clarity and emotional tone of the arguments presented---turning complex social commentary into an accessible and compelling visual narrative.
+
+{{< video https://www.youtube.com/embed/n0J641t6IUE?si=qjfJfLo7WTwzktS1 >}}
 

### 2025-08-05 index.qmd
Update with proper downloads
Resume Update

@@
 
-Hello there!
-My name is Marzuki Nooranas \[[Resume](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)\] - or *Marz* for short!
-I am currently in my 3rd year, majoring in Sociology and Interactive Media Development!
+Hello there! My name is Marzuki Nooranas or *Marz* for short! I am currently in my final year, majoring in Sociology and Interactive Media Development!
 

### 2025-08-13 index.qmd
Update

@@
 ```
+
 ::: tiktok-container
@@
 ```
+
 ## Contact Details
@@
 
-Resume - [Download](https://raw.githubusercontent.com/mrzknrns/mrzknrns.github.io/c446afc4b2d7902cfc76a22458cbc7789d1a09d7/MARZUKI_SANIP_RESUME.pdf)
+Resume - [Download](MARZUKI_SANIP_RESUME_Updated.pdf)
 
